\section{SmallWood Proof-System Details}
\label{app:smallwood}

This appendix recalls the SmallWood proof stack and provides algorithmic details used by our instantiations. The main
text treats SmallWood as a black box; here we summarize the DECS/LVCS/PCS/PIOP layers and the Fiat--Shamir compilation,
following \cite{EPRINT:FenRiv25b}.

\newcommand{\NTT}{\mathrm{NTT}}

\subsection{Domains and packing}
Fix a base field \(\Fq\), an evaluation set \(\Omega\subset\Fq\) of size \(s\), and a disjoint tail set
\(\Omega'\subset\Fq\setminus\Omega\) of size \(\ell\). A witness row is interpolated into a polynomial of degree
\(\le s+\ell-1\) whose values on \(\Omega\) are the packed coordinates and whose values on \(\Omega'\) are random masks
(HVZK).

\subsection{DECS (Degree-Enforcing Commitment Scheme)}
DECS commits to evaluations of witness polynomials and enforces that they come from low-degree polynomials rather than
arbitrary vectors. Commitments are implemented via a Merkle tree over an NTT-sized domain, and degree soundness is
obtained by checking masked low-degree relations at verifier-chosen indices.

\begin{algorithm}[H]
\caption{\textsf{DECS.DeriveGamma}(\(\mathsf{root},\eta,r,q\)) \(\to \Gamma\) (verifier and prover)}
\label{alg:decs-derivegamma}
\begin{algorithmic}[1]
\State Initialize counter \(ctr\gets 0\); let \(L\gets \big\lfloor \frac{2^{64}}{q}\big\rfloor\cdot q\).
\For{\(k=0\) to \(\eta-1\)}
  \For{\(j=0\) to \(r-1\)}
    \Repeat
      \State \(x \gets \textsf{SHA256}(\mathsf{root}\ \|\ \textsf{LE64}(ctr))\) interpreted as a 64-bit integer
      \State \(ctr\gets ctr+1\)
    \Until{\(x < L\)}
    \State \(\Gamma_{k,j}\gets x \bmod q\)
  \EndFor
\EndFor
\State \Return \(\Gamma\)
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsf{DECS.VerifyEval}(\(\mathsf{root},\Gamma,R,\mathsf{open}\)) (verifier)}
\label{alg:decs-verifyeval}
\begin{algorithmic}[1]
\Require Domain size \(N\), modulus \(q\), mask count \(\eta\), committed row count \(r\).
\For{each opened index \(e\)}
  \State Verify Merkle authentication for \(e\) against \(\mathsf{root}\); reject on failure.
  \For{each mask row \(k<\eta\)}
    \State Check \(R_k^\star[e] \stackrel{?}{=} M_k(e) + \sum_{j=0}^{r-1}\Gamma_{k,j}\,P_j(e)\pmod q\).
  \EndFor
\EndFor
\State \Return accept
\end{algorithmic}
\end{algorithm}

\subsection{LVCS (Linear Vector Commitments)}
LVCS commits to packed witness rows and supports succinct openings of \(\Fq\)-linear forms of those rows. SmallWood uses
LVCS both as a routing/batching layer and as the core of its hash-based PCS: the verifier requests openings of linear
forms that correspond to evaluating constraint residuals at verifier-chosen points, and DECS enforces that opened values
come from low-degree polynomials.

\begin{algorithm}[H]
\caption{\textsf{LVCS.CommitInitWithParams}(\(\mathrm{ringQ},\{r_j\}_{j<r},\ell,\mathrm{params}\)) \(\to (\mathsf{root},\mathsf{ProverKey})\) (prover)}
\label{alg:lvcs-commitinit}
\begin{algorithmic}[1]
\Require Ring \(R_q\) of size \(N\), packed rows \(r_j\in\Fq^{n_{\mathrm{cols}}}\), tail length \(\ell>0\).
\State Sample \(\mathrm{mask}_j\getsunif \Fq^{\ell}\) for each row \(j\) (HVZK tails).
\State Interpolate each row to \(P_j(X)\gets \textsf{interpolateRow}(\mathrm{ringQ},r_j,\mathrm{mask}_j,n_{\mathrm{cols}},\ell)\).
\State Commit to \(\{P_j\}\) via DECS and obtain Merkle root \(\mathsf{root}\).
\State Derive \(\Gamma\gets \textsf{DECS.DeriveGamma}(\mathsf{root},\eta,r,q)\) and cache values needed for openings.
\State \Return \((\mathsf{root},\mathsf{ProverKey})\).
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsf{LVCS.CommitStep1}(\(\mathsf{root}\)) \(\to \Gamma\) (verifier)}
\label{alg:lvcs-commitstep1}
\begin{algorithmic}[1]
\State Store \(\mathsf{root}\) and derive \(\Gamma\gets \textsf{DECS.DeriveGamma}(\mathsf{root},\eta,r,q)\).
\State \Return \(\Gamma\).
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsf{LVCS.CommitStep2}(\(\{R_k\}_{k<\eta}\)) \(\to\) accept/reject (verifier)}
\label{alg:lvcs-commitstep2}
\begin{algorithmic}[1]
\For{each mask row \(R_k\)}
  \State Reject if \(\deg(R_k) > d\) (degree guard before openings).
\EndFor
\State \Return accept.
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsf{LVCS.EvalInitMany}(\(\mathrm{ringQ},\mathsf{ProverKey},\{\mathrm{Coeffs}_k\}_{k<m}\)) \(\to \{\bar v_k\}_{k<m}\) (prover)}
\label{alg:lvcs-evalinit}
\begin{algorithmic}[1]
\Require Linear forms \(\mathrm{Coeffs}_k\in\Fq^{r}\) for \(k=0,\dots,m-1\).
\State Let \(\ell\gets |\mathrm{mask}_j|\).
\For{\(k=0\) to \(m-1\)}
  \State Initialize \(\bar v_k\gets 0\in\Fq^{\ell}\).
  \State Set \(\bar v_k \gets \sum_{j=0}^{r-1} \mathrm{Coeffs}_k[j]\cdot \mathrm{mask}_j \in \Fq^{\ell}\).
\EndFor
\State \Return \(\{\bar v_k\}_{k<m}\).
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsf{LVCS.ChooseE}(\(\ell,n_{\mathrm{cols}}\)) \(\to E\) (verifier)}
\label{alg:lvcs-choosee}
\begin{algorithmic}[1]
\Require Ring size \(N\); packed domain size \(n_{\mathrm{cols}}=|\Omega|\); masked slab indices \([n_{\mathrm{cols}},n_{\mathrm{cols}}+\ell)\).
\State Sample \(E\subset \{n_{\mathrm{cols}}+\ell,\dots,N-1\}\) uniformly without replacement with \(|E|=\ell\).
\State \Return \(E\).
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsf{LVCS.EvalFinish}(\(\mathsf{ProverKey},E\)) \(\to \mathsf{Opening}\) (prover)}
\label{alg:lvcs-evalfinish}
\begin{algorithmic}[1]
\State \(\mathsf{open}\gets \mathsf{ProverKey}.\mathrm{DecsProver}.\textsf{EvalOpen}(E)\).
\State \Return \(\mathsf{Opening}\{\mathrm{DECSOpen}=\mathsf{open}\}\).
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsf{LVCS.EvalStep2}(\(\{\bar v_k\},E,\mathsf{open},C,v_{\mathrm{targets}}\)) (verifier)}
\label{alg:lvcs-evalstep2}
\begin{algorithmic}[1]
\Require Coeffs \(C\in\Fq^{m\times r}\), public prefixes \(v_{\mathrm{targets}}\in(\Fq^{n_{\mathrm{cols}}})^{m}\).
\State Split \(\mathsf{open}\) into mask openings for \([n_{\mathrm{cols}},n_{\mathrm{cols}}+\ell)\) and tail openings at \(E\).
\State Verify the DECS openings (degree soundness and Merkle authentication); reject on failure.
\For{each \(k<m\) and each masked index \(i<\ell\)}
  \State Check \(\sum_{j=0}^{r-1} C[k,j]\cdot \mathsf{maskOpen.Pvals}[i][j] \stackrel{?}{=} \bar v_k[i]\pmod q\).
\EndFor
\State Reconstruct each batched polynomial \(Q_k(X)\) from its \(\Omega\)-prefix \(v_{\mathrm{targets}}[k]\) and mask tail \(\bar v_k\).
\State Check tail consistency of \(Q_k\) against the opened linear combinations at points in \(E\).
\State \Return accept.
\end{algorithmic}
\end{algorithm}

\subsection{LVCS and PCS/PIOP}
LVCS provides linear opening queries to committed rows and is used to implement the polynomial oracle interface needed
by PIOPs. SmallWood combines LVCS with DECS (for degree enforcement) to obtain a hash-based PCS.

\subsection{What DECS/LVCS/PCS bind in ARC-SPRUCE}\label{app:smallwood-binds}
At a high level, the SmallWood stack provides a single commitment that
simultaneously binds \emph{all committed witness rows} of a statement, and it
enforces that every opened value is consistent with a low-degree polynomial
view of those rows. In ARC-SPRUCE this binding is used in three complementary
ways:
\begin{itemize}[leftmargin=1.25em]
  \item \textbf{Row binding and low degree (DECS).} DECS ensures that the
  prover cannot answer openings using high-degree ``fake'' vectors: each
  committed row must correspond to a degree-\(\le s+\ell-1\) polynomial that
  matches the packed values on \(\Omega\) and the masked tails on
  \(\Omega'\).
  \item \textbf{Replay binding across subsystems (LVCS).} LVCS is used to
  request verifier-chosen linear openings of the committed rows. In issuance
  these same openings are reused to replay carrier membership, carrier-to-alias
  decode bridges, commitment, centering, packing, the transform-domain
  public-target hash, and the four aggregated non-sign transform bridges. In
  showing the same openings are reused to replay signature digit membership,
  the direct limb-to-\(\widehat T_0\) bridge, the non-sign bridges to
  \(\widehat m,\widehat R_0,\widehat R_1\), the replay residual, and the
  PRF companion constraints.
  \item \textbf{No witness splitting (single PCS commitment).} Because all
  committed rows live under one PCS root, the prover cannot use inconsistent
  witnesses for different subsystems. In issuance the same committed carriers
  determine the committed decoded aliases and the replay-facing hats. In
  showing the same committed message carrier \(C^M\) simultaneously determines
  the decoded message used in packing and PRF key binding and the transform
  alias \(\widehat m\), while the same committed limb rows determine the
  only committed signature replay row \(\widehat T_0\).
\end{itemize}
This is the current binding invariant of the implementation: every replay check
is expressed as a residual function of committed row openings, and every
deterministic link needed by replay is either an explicit committed alias row
or an explicit PACS family.

\subsection{Openings we request in issuance vs showing}\label{app:smallwood-openings}
Both proofs in ARC-SPRUCE follow the same pattern: the prover commits to all
statement rows as explicit-domain polynomials, the verifier derives
Fiat--Shamir challenges, and the prover opens the committed rows at
verifier-chosen points. The verifier then recomputes the residuals of the
active constraint families from those openings and checks the parallel replay
identities at \(E'\) together with the aggregated \(\Omega\)-sum identities.

\paragraph{Issuance (pre-sign).}
The committed issuance witness consists of
\[
  C^M,\ C^{\mathrm{preRU}},\ C^{\mathrm{preR}},\ C^{\mathrm{ctr}},\ C^J,
\]
\[
  M,\ K,\ R_U^0,\ R_U^1,\ R,\ R_0,\ R_1,\ J_0,\ J_1,
\]
\[
  \widehat M,\ \widehat K,\ \widehat R_0,\ \widehat R_1.
\]
The public blind-signature target remains public as a coefficient-domain ring
element \(T\), and the verifier derives its public theta-lift \(T^\Theta\).
The verifier requests openings sufficient to replay:
\begin{enumerate}[leftmargin=1.25em]
  \item carrier membership on the five committed carriers,
  \item carrier-to-alias decode bridges from those carriers to the nine
  committed alias rows,
  \item commitment, centering, and packing on the committed alias rows,
  \item the transform-domain public-target hash residual on
  \(\widehat M,\widehat K,\widehat R_0,\widehat R_1\) against public
  \(B^\Theta\) and public \(T^\Theta\),
  \item the four aggregated non-sign transform bridges
  \(M\!\to\!\widehat M\), \(K\!\to\!\widehat K\),
  \(R_0\!\to\!\widehat R_0\), and \(R_1\!\to\!\widehat R_1\).
\end{enumerate}
Because all of these checks are replayed from the same committed rows, the
pre-sign proof binds the public target \(T\) to the commitment opening, the
centering step, and the exact transform images of the committed non-sign rows.

\paragraph{Showing (post-sign).}
The committed showing witness is smaller and already reduced to the
theorem-essential replay surface. It consists of:
\begin{enumerate}[leftmargin=1.25em]
  \item cert-side signature limb rows \(L_{c,b,\ell}\),
  \item the committed carriers \(C^M\) and \(C^{\mathrm{ctr}}\),
  \item the committed replay aliases
  \(\widehat T_0,\widehat m,\widehat R_0,\widehat R_1\),
  \item the packed PRF companion rows.
\end{enumerate}
There are no committed \(\widetilde S\) rows, no committed \(\widehat S\)
rows, no semantic \(U\) rows, and no committed witness row for the target
\(T\). The verifier requests openings sufficient to replay:
\begin{enumerate}[leftmargin=1.25em]
  \item signature digit membership on the limb rows,
  \item the direct aggregated limb-to-\(\widehat T_0\) bridge,
  \item the aggregated non-sign transform bridges
  \((M+K)\!\to\!\widehat m\),
  \(R_0\!\to\!\widehat R_0\), and
  \(R_1\!\to\!\widehat R_1\),
  \item the transform-domain replay residual on
  \(\widehat T_0,\widehat m,\widehat R_0,\widehat R_1\),
  \item packing and carrier membership on the decoded non-sign rows,
  \item PRF key binding, grouped checkpoint constraints, and final tag binding
  on the packed companion rows.
\end{enumerate}
The decoded message and centered-randomness rows remain virtual decode images of
the committed carriers, and the virtual packed signature source is reconstructed
linearly from the limb rows. The direct bridge to \(\widehat T_0\) is what
lets the verifier replay the showing equation from one committed signature-side
row instead of from a larger semantic signature surface.

\paragraph{Internal \(\Omega\)-sum check.}
The \(\Omega\)-sum check is active in both of our proofs. In issuance it
enforces the four non-sign transform bridges. In showing it enforces the direct
limb-to-\(\widehat T_0\) bridge and the three non-sign transform bridges; the
PRF constancy family is present only in the general model and is empty in the
shipped packed-companion path. Thus the \(\Sigma_\Omega\) check is not merely a
generic PCS safeguard: it is part of the active statement layer of both
issuance and showing.

\subsection{PACS/PIOP interface (used by our statements)}
SmallWood’s PACS/PIOP layer checks that constraint polynomials vanish on \(\Omega\) (and at random points outside
\(\Omega\)), by committing to witness rows and mask polynomials and then opening them at verifier-chosen coordinates.
The following algorithms summarize the high-level structure used in our proofs.

\begin{algorithm}[H]
\caption{\textsf{PACS.PIOPCommitOracle}\(_{\mathrm{Prover}}(\textsf{params})\to \textsf{pcsCom}\)}
\label{alg:pacs-commitoracle}
\begin{algorithmic}[1]
\State Interpolate witness rows into \(P_1,\ldots,P_n\in\Fq[X]_{\le s+\ell'-1}\) with \(\ell'\) random blind evaluations outside \(\Omega\).
\State Sample mask polynomials \(M_1,\ldots,M_\rho\in\Fq[X]_{\le d_Q}\) such that \(\sum_{\omega\in\Omega} M_i(\omega)=0\) for all \(i\).
\State Commit to \(P\Vert M\) via PCS (implemented through LVCS/DECS); obtain \(\textsf{pcsCom}\).
\State \Return \(\textsf{pcsCom}\).
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsf{PACS.PIOPBatchCombine}\(_{\mathrm{Prover}}(\textsf{pcsCom},\Gamma')\to Q\)}
\label{alg:pacs-batchcombine}
\begin{algorithmic}[1]
\State Using \(P,M\), form batched polynomials
\[
Q_i(X) \;=\; M_i(X) + \sum_j \Gamma'_{i,j}(X)\,F_j(X) + \sum_u \gamma'_{i,u}\,F'_u(X),
\]
where \(F_j\) and \(F'_u\) are the parallel and aggregated constraint polynomials evaluated on \(P\).
\State \Return \(Q=(Q_1,\ldots,Q_\rho)\).
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{\textsf{PACS.PIOPOpenAndCheck}(\(\textsf{pcsCom},Q\)) (verifier)}
\label{alg:pacs-openandcheck}
\begin{algorithmic}[1]
\State Sample a query set \(E'\subset S\) with \(|E'|=\ell'\) (Fiat--Shamir in NIZK).
\State Verify PCS openings of \(P\) and \(M\) at \(E'\) (via LVCS/DECS); reject on failure.
\State Check that each \(Q_i(e)\) matches its definition from \(M_i(e)\) and the constraint evaluations at \(e\in E'\).
\State Check the masked \(\Omega\)-sum test \(\sum_{\omega\in\Omega} Q_i(\omega)=0\) for all \(i\).
\State \Return accept/reject.
\end{algorithmic}
\end{algorithm}

In the current ARC instantiation, the prover also supplies formal coefficient
representations of the active parallel and aggregated families in
explicit-domain mode. This is crucial for the transform-bridge statements:
decode compositions, theta-lifted replay rows, and aggregated bridge
polynomials must be replayed as actual polynomial identities at \(E'\), not as
naive pointwise products on \(\Omega\).

\subsection{Fiat--Shamir compilation}
SmallWood compiles the interactive protocol to a NIZK using Fiat--Shamir with grinding to obtain challenges with
all-zero prefixes, as in \cite{EPRINT:FenRiv25b}. The generic wrapper remains
unchanged, but the active ARC instantiation now uses both
\(F_{\mathrm{par}}\neq\emptyset\) and \(F_{\mathrm{agg}}\neq\emptyset\) in
issuance and showing. The verifier therefore derives challenges for the same
batched PIOP, then checks both replay identities at \(E'\) and the active
\(\Omega\)-sum constraints for the transform bridges.

\begin{algorithm}[H]
\caption{\textsf{PACS.ToNIZK} (Fiat--Shamir wrapper with grinding)}
\label{alg:pacs-tonizk}
\begin{algorithmic}[1]
\State Sample \(\textsf{salt}\getsunif\{0,1\}^{2\lambda}\).
\State Derive challenges by hashing the transcript with grinding counters to obtain required prefix properties.
\State Output PCS/LVCS/DECS openings and any required batched values; the verifier recomputes challenges and checks.
\end{algorithmic}
\end{algorithm}
