\section{From Blind Signatures to ARC}
\label{sec:arc-construction}

This section turns the blind-issuance protocol of Section~\ref{sec:blind-signature} into an anonymous
rate-limited credential.  The holder signs the full message $\vecmu=\vecm\Vert\veck$, where $\vecm$ is the
attribute vector and $\veck$ is a uniformly sampled secret PRF key.

\paragraph{Credential witness.}
After successful issuance the holder stores
\[
  \credential=(\vecu,\vecm,\veck,r_0,r_1),
\]
where $\mA\vecu=T$ and
\[
  T=B_0+B_1(\vecm\Vert\veck)+B_2r_0+Z,
  \qquad
  (B_3-r_1)\Had Z=1.
\]
The value $Z$ may either be stored or recomputed from $r_1$ when showing the credential.

\subsection{Rate limiting via the signed key}
Rate limiting is implemented by deterministic tags derived from the signed secret key $\veck$.  For a public
nonce $\nonce\in\mathcal D$, the holder computes
\[
  \prftag=\PRF(\veck,\nonce).
\]
If the holder reuses a nonce, the tag repeats and the verifier can reject by consulting local state.  For fresh
nonces, PRF security makes the tags computationally independent of previous tags.  Since $\veck$ is part of
the signed message, the holder cannot change the PRF key without forging a new credential.

\subsection{ARC protocol}
\label{subsec:arc-protocol}
The setup and issuer-key-generation algorithms are those of Section~\ref{subsec:bs-protocol}.

\paragraph{Issue.}
The holder executes the issuance protocol on message $\vecmu=\vecm\Vert\veck$.  If the final check
$\mA\vecu=T$ succeeds, it stores $\credential=(\vecu,\vecm,\veck,r_0,r_1)$.

\paragraph{Show.}
On input $\credential$ and nonce $\nonce$, the holder computes
\[
  Z=(B_3-r_1)^{-1},\qquad \prftag=\PRF(\veck,\nonce),
\]
and produces a NIZK proof $\nizkShow$ of knowledge of
\[
  \vecu,\vecm,\veck,r_0,r_1,Z
\]
such that
\begin{align*}
  &(B_3-r_1)\Had Z=1,\\
  &\mA\vecu=B_0+B_1(\vecm\Vert\veck)+B_2r_0+Z,\\
  &\prftag=\PRF(\veck,\nonce),
\end{align*}
and all hidden values satisfy the relevant bounds.  It outputs
\[
  \presentation=(\nonce,\prftag,\nizkShow).
\]

\paragraph{Verify.}
The verifier checks $\nizkShow$ against the public statement containing $(\vk,B,\nonce,\prftag)$ and the
public bounds.  If the proof rejects, verification returns reject.  If $(\nonce,\prftag)$ is already present in
verifier state, verification also rejects.  Otherwise the verifier stores $(\nonce,\prftag)$ and accepts.

\subsection{Concrete PRF instantiation}
\label{subsec:poseidon-prf}
We instantiate the PRF using the Poseidon2-like construction of Definition~\ref{def:poseidon-prf}.  Algorithm~\ref{alg:poseidon-prf}
summarizes the computation.

\begin{algorithm}[h]
\caption{$\PRF(\veck,\vecn)$: Poseidon2-like with feed-forward and truncation}\label{alg:poseidon-prf}
\begin{algorithmic}[1]
\State $x\gets \veck\Vert\vecn$; $x^{(0)}\gets x$
\For{$i=1$ to $R_F/2$}
  \State $x\gets E_i(x)$
\EndFor
\For{$i=1$ to $R_P$}
  \State $x\gets I_i(x)$
\EndFor
\For{$i=R_F/2+1$ to $R_F$}
  \State $x\gets E_i(x)$
\EndFor
\State $y\gets x+x^{(0)}$
\State \Return $\Tr_{\ell_{\mathsf{tag}}}(y)$
\end{algorithmic}
\end{algorithm}

In the showing proof, the equation $\prftag=\PRF(\veck,\nonce)$ is enforced with the checkpointed
arithmetization described in Section~\ref{subsec:prf-checkpointed} and Appendix~\ref{app:prf}.

\subsection{Security decomposition}
\label{subsec:arc-security-decomp}
The ARC layer combines the following ingredients:
\begin{enumerate}[leftmargin=1.25em]
  \item the non-blind signature security imported in Lemma~\ref{lem:vsis-unforgeability};
  \item issuer-view hiding of the issuance surface from Proposition~\ref{prop:bs-issuer-view-hiding};
  \item one-more unforgeability of the blind-issuance protocol;
  \item knowledge soundness and zero knowledge of the showing NIZK;
  \item correctness and pseudorandomness of the PRF; and
  \item verifier-side state recording previously accepted $(\nonce,\prftag)$ pairs.
\end{enumerate}
The first two ingredients are established in the main text under the stated assumptions.  The third remains
a separate reduction goal.  The last item is an application-layer enforcement rule rather than a standalone
cryptographic assumption.

\paragraph{Conditional policy soundness.}
Knowledge soundness of the showing proof yields a witness satisfying the BB-tran signature relation and
the PRF relation.  Assuming one-more unforgeability of the blind-issuance layer, an adversary cannot obtain
more valid credential witnesses than issuance sessions allow.  Since $\prftag=\PRF(\veck,\nonce)$ is uniquely
determined by the signed key and nonce, a verifier that records spent $(\nonce,\prftag)$ pairs rejects same-nonce
replays deterministically.

\paragraph{Conditional presentation unlinkability.}
For distinct fresh nonces, zero knowledge hides the credential witness and PRF security makes the public tags
pseudorandom.  Presentation unlinkability also relies on issuance-layer privacy because the adversary may
control the issuer during issuance.  Under Proposition~\ref{prop:bs-issuer-view-hiding}, showing transcripts
are unlinkable up to the intended nonce-reuse caveat.

\paragraph{Attribute privacy and selective disclosure.}
The message part $\vecm$ can encode attributes.  The showing NIZK can be extended to prove predicates over
$\vecm$ or to selectively reveal components without changing the issuance protocol.
