\section{Blind Signature Construction}
\label{sec:blind-signature}

This section presents the vSIS-based blind signature that underlies ARC-SPRUCE. It combines the Ajtai commitment of
Section~\ref{subsec:commitments}, the trapdoor rational hash of Definition~\ref{def:rational-hash}, and the NIZK-ARK of
Definition~\ref{def:nizk-ark}. The signed message is always
\[
  \vecmu=\vecm\Vert \veck,
\]
where \(\vecm\) denotes the attribute payload and \(\veck\) is a holder-generated secret PRF key used later for rate
limiting.
% Carsten (10-04): The signed message is denoted as \vecmu.

\subsubsection{Randomizing the rational-hash witness}
In the protocol, \(\Holder\) first commits to
\[
  \vecw=[\vecmu\Vert \vecr_0^{\Holder}\Vert \vecr_1^{\Holder}\Vert \bar\vecr]^\top,
\]
where \((\vecr_0^{\Holder},\vecr_1^{\Holder})\) are the holder contributions to the rational-hash witness and
\(\bar\vecr\) is fresh commitment randomness. To satisfy the commitment bounds, we require
\(\|\vecw\|_\infty\le \BoundMsg\).

The issuance process then uses a two-party randomness generation step: the issuer samples
\((\vecr_0^{\Issuer},\vecr_1^{\Issuer})\), and the joint witness is obtained coefficient-wise by
\[
  \vecr_0=\centerfunc(\vecr_0^{\Holder}+\vecr_0^{\Issuer}),\qquad
  \vecr_1=\centerfunc(\vecr_1^{\Holder}+\vecr_1^{\Issuer}).
\]
Appendix~\ref{app:defs} records the centering map and its uniformity property.

\subsubsection{Blind signature protocol}
\label{subsec:issuance-protocol}
\label{subsec:bs-protocol}
We assume \(\nizkscheme=(\ZKProve,\ZKVerify)\) is a NIZK for the relations below,
\(\ComScheme=(\ComSetup,\Commit,\ComVerify)\) is the Ajtai commitment scheme, and
\[
  \TDRH=(\Setup,\TrapGen,\mathsf{Eval},\SampPre)
\]
is the trapdoor rational-hash interface from Definition~\ref{def:bbs-rational-hash}. Public setup outputs the hash key
\(B\), while issuer key generation outputs the trapdoored signing matrix \(\mA\).

\paragraph{Abstract issuance and signature relations.}
At the protocol level, issuance is described by the following abstract witness statement.
We write \(R_{\mathrm{Issue}}^{\mathrm{abs}}(x,w)=1\) iff
\[
\begin{aligned}
  x&=\bigl(\ComPublicParam,\vecc,T,(\vecr_0^{\Issuer},\vecr_1^{\Issuer}),B\bigr),\\
  w&=(\vecmu,\vecr_0^{\Holder},\vecr_1^{\Holder},\bar\vecr),\\
  \ComPublicParam&=(\mACom,\BoundMsg),\\
  \vecc&=\mACom\cdot[\vecmu\Vert \vecr_0^{\Holder}\Vert \vecr_1^{\Holder}\Vert \bar\vecr]^\top,\\
  \|\vecmu\|_\infty,\|\vecr_0^{\Holder}\|_\infty,\|\vecr_1^{\Holder}\|_\infty,\|\bar\vecr\|_\infty&\le \BoundMsg,\\
  \vecr_0&=\centerfunc(\vecr_0^{\Holder}+\vecr_0^{\Issuer}),\\
  \vecr_1&=\centerfunc(\vecr_1^{\Holder}+\vecr_1^{\Issuer}),\\
  T&=h_{\vecmu,(\vecr_0,\vecr_1)}(B).
\end{aligned}
\]

The issued signature relation remains the abstract relation
\[
R_{\mathrm{Sign}}(x,w)=1
\iff
x=(\vecmu,\mA,B,\BoundMsg,\BoundSig),\quad w=(\vecu,\vecr_0,\vecr_1),
\]
\[
  \|\vecr_0\|_\infty,\|\vecr_1\|_\infty \le \BoundMsg,
  \qquad
  \|\vecu\|_\infty \le \BoundSig,
\]
\[
  h_{\vecmu,(\vecr_0,\vecr_1)}(B)\neq\bot,
  \qquad
  \mA\vecu=h_{\vecmu,(\vecr_0,\vecr_1)}(B).
\]
The concrete pre-sign proof used by the protocol is a compiled SmallWood relation over committed rows and public lifts.
We defer that compiled statement to Section~\ref{subsec:presign-compiled}; the present section keeps the issuance
protocol at the abstract witness level.

We now define the blind-signature algorithms.
\begin{comment}
Preserved from Carsten's 10-04 source: an older proof-carrying-signature presentation introduced the explicit relation
macros \(\relIssueBS\) and \(\relSign\), defined the blind-signature protocol directly in terms of those relations, and
packaged the final signature as a proof object \(\nizkSign\). The current live text keeps the later theorem-disciplined
abstract/compiled split, but the compatibility macros and the historical formulation are intentionally retained in
source.
\end{comment}
\begin{description}
  \item[$\Setup(\SecParam)$:] Fix the global ring parameters. Run
  \[
    (\mACom,\BoundMsg)\gets \ComScheme.\ComSetup(\SecParam)
  \]
  and
  \[
    (B,\mathcal{M},\mathcal{X},\delta,\BoundMsg,\BoundSig)\gets \TDRH.\Setup(\SecParam).
  \]
  Output
  \[
    \PublicParamsBS=(\mACom,B,\mathcal{M},\mathcal{X},\delta,\BoundMsg,\BoundSig).
  \]

  \item[$\IKeyGen()$:] Compute \((\mA,\trapdoor)\gets \TDRH.\TrapGen(\SecParam)\) and output
  \[
    \vk=\mA,\qquad \sk=\trapdoor.
  \]

  \item[$\Issue$:] The issuer \(\Issuer\) holds \(\sk\); the holder \(\Holder\) holds \(\vecm,\vk\).
  \begin{enumerate}[leftmargin=1.25em]
    \item \(\Holder\) samples \(\veck,\vecr_0^{\Holder},\vecr_1^{\Holder},\bar\vecr\) coefficient-wise in
    \([ -\BoundMsg,\BoundMsg]\) and sets \(\vecmu=\vecm\Vert \veck\).
    \item \(\Holder\) computes
    \[
      \vecc\gets \mACom\cdot[\vecmu\Vert \vecr_0^{\Holder}\Vert \vecr_1^{\Holder}\Vert \bar\vecr]^\top
    \]
    and sends \(\vecc\) to \(\Issuer\).
    \item \(\Issuer\) samples \(\vecr_0^{\Issuer},\vecr_1^{\Issuer}\) coefficient-wise in
    \([ -\BoundMsg,\BoundMsg]\) and sends them to \(\Holder\).
    \item \(\Holder\) computes
    \[
      \vecr_0\gets \centerfunc(\vecr_0^{\Holder}+\vecr_0^{\Issuer}),\qquad
      \vecr_1\gets \centerfunc(\vecr_1^{\Holder}+\vecr_1^{\Issuer}),
    \]
    checks whether \(h_{\vecmu,(\vecr_0,\vecr_1)}(B)=\bot\), and aborts/restarts if so. Otherwise it computes the public target
    \[
      T\gets h_{\vecmu,(\vecr_0,\vecr_1)}(B).
    \]
    \item \(\Holder\) computes \(\nizkIssue\gets \nizkscheme.\ZKProve(w,x)\) for the issuance statement above, with witness
    \[
      w=(\vecmu,\vecr_0^{\Holder},\vecr_1^{\Holder},\bar\vecr)
    \]
    and statement
    \[
      x=(\ComPublicParam,\vecc,T,(\vecr_0^{\Issuer},\vecr_1^{\Issuer}),B),
    \]
    and sends \((T,\nizkIssue)\) to \(\Issuer\).
    \item \(\Issuer\) verifies \(\nizkIssue\). If verification fails, it aborts.
    Otherwise it computes
    \[
      \vecu\gets \TDRH.\SampPre(\trapdoor,T)
    \]
    and sends \(\vecu\) to \(\Holder\).
    \item \(\Holder\) checks \(\|\vecu\|_\infty\le \BoundSig\) and \(\mA\vecu=T\). If so, it outputs
    \[
      \sig=(\vecu,\vecr_0,\vecr_1)
    \]
    on message \(\vecmu=\vecm\Vert \veck\); otherwise it aborts.
  \end{enumerate}

  \item[$\Verify(\vk,\vecmu,\sig)$:] Let \(\vk=\mA\). Parse \(\sig=(\vecu,\vecr_0,\vecr_1)\). Accept iff
  \[
    \bigl((\vecmu,\mA,B,\BoundMsg,\BoundSig),(\vecu,\vecr_0,\vecr_1)\bigr)\in R_{\mathrm{Sign}}.
  \]
\end{description}

For ARC, the holder does not reveal \(\sig\) directly. Section~\ref{sec:arc-construction} instead states the abstract
showing witness relation in zero knowledge, while Section~\ref{sec:smallwood-model} later specifies the compiled
SmallWood realization that binds \(\veck\) to the PRF tag.
% For ARC, the holder does not reveal \(\sig\) directly. Section~\ref{sec:arc-construction} instead proves the relation
% \(\relSign\) in zero knowledge while keeping \(\veck,\vecr_0,\vecr_1\) hidden and binding \(\veck\) to the PRF tag.

\subsubsection{Security}
\begin{proposition}[Correctness]
Assume the pre-sign NIZK is complete and the trapdoor sampler is correct. Then an honest execution of \(\Issue\)
outputs a signature \(\sig\) that is accepted by \(\Verify\), except with negligible failure probability coming from the
trapdoor sampler or an inadmissible hash evaluation.
\end{proposition}

\begin{proof}
By honest target derivation, the holder computes \(T\) only after checking that
\(h_{\vecmu,(\vecr_0,\vecr_1)}(B)\neq\bot\), and then sets
\[
T=h_{\vecmu,(\vecr_0,\vecr_1)}(B).
\]
The honest witness therefore satisfies the abstract issuance statement above, so completeness of the pre-sign proof
implies that the issuer accepts. By correctness of \(\SampPre\), the returned \(\vecu\) satisfies \(\mA\vecu=T\) and
the public shortness bound except with negligible probability. Hence \(\sig=(\vecu,\vecr_0,\vecr_1)\) satisfies
\(R_{\mathrm{Sign}}\).
\end{proof}

\cb{todo: add more statements and proofs here once definitions are settled in prelims.}

\begin{remark}[Security status of the blind protocol]\label{rem:blind-security-roadmap}
The non-blind hash-and-preimage signature layer underlying this protocol is justified by the DKLW25 reduction summarized
in Lemma~\ref{lem:vsis-unforgeability}. For the blind protocol itself, the only theorem-backed property proved in the
present draft is honest-party correctness. A proof of one-more unforgeability would still have to combine the
extractability of the pre-sign proof, the hiding of the Ajtai commitment, the algebraic correctness of the centering
step, and an interactive one-more hardness statement that genuinely matches the issuance oracle. A proof of blindness
would still have to combine the same commitment-hiding and proof zero-knowledge ingredients with a simulation argument
for the issuer view. Accordingly, the blind protocol is presented here as a construction with defined goals and an
explicit reduction roadmap, not as a layer for which blindness or one-more unforgeability has already been reduced.
\end{remark}

\begin{comment}
\begin{remark}[Security roadmap]
The non-blind hash-and-preimage signature layer underlying this protocol is justified by the DKLW25 reduction discussed
in Remark~\ref{rem:vsis-unforgeability}. For the blind protocol itself, the intended route is to combine straightline
extractability of the pre-sign proof with an interactive \(\mathsf{GenISIS}_f\)-style assumption for
\[
  f(B,\vecmu,(\vecr_0,\vecr_1))=h_{\vecmu,(\vecr_0,\vecr_1)}(B),
\]
while using statistical hiding of the Ajtai commitment and zero knowledge of the pre-sign proof in the blindness
argument. This explains why the construction targets one-more unforgeability and blindness, but we do not claim a
completed reduction for either property here.
\end{remark}
\end{comment}
