\section{SmallWood Programming Model}
\label{sec:smallwood-model}
\label{sec:smallwood}

This section specifies the compiled SmallWood relations used by ARC-SPRUCE. Its role is to record the committed witness
surfaces, public lifts, and PACS constraint families certified by the issuance and showing proofs. Throughout, SmallWood
certifies only these compiled relations: namely, relations over committed witness rows, public inputs, and PACS
constraints derived from them. Whenever later sections use a coefficient-domain consequence of a showing proof, they do so
only through the theorem suite in Section~\ref{subsec:statement-strength}. Detailed row inventories, exact PACS splits,
and proof-stack geometry are deferred to Appendix~\ref{app:smallwood}.

At the protocol layer, issuance and showing are quotient-ring witness statements. The present section records their
compiled realizations. In issuance, the compiled relation keeps the target \(T\) public and proves a cleared-denominator
statement about hidden committed rows. In showing, the compiled relation commits a cert-side (the subset of witness rows 
encoding the signature relation) signature surface, coefficient-domain source rows, exact replay-image blocks, and PRF 
companion rows. The verifier checks the replay-space statement on those replay-image blocks, while
Section~\ref{subsec:statement-strength} transports that replay-space statement back to the coefficient-domain identity 
used later in the paper.

\subsection{Proof-language interface}
\label{subsec:smallwood-interface}
Fix an evaluation set \(\Omega=\{\omega_1,\ldots,\omega_s\}\subset \Fq\) and a disjoint set of blinding points
\(\Omega'\subset \Fq\setminus \Omega\). A witness is arranged as a matrix
\[
W\in \Fq^{n\times s},
\]
whose rows are interpolated into low-degree polynomials
\[
P_1(X),\ldots,P_n(X)\in \Fq[X]
\]
satisfying
\[
P_i(\omega_k)=W_{i,k}\qquad\text{for all }\omega_k\in\Omega,
\]
and taking random values on \(\Omega'\) in order to achieve honest-verifier zero knowledge. SmallWood then commits to
these row polynomials and proves PACS constraints by opening verifier-chosen linear maps of the committed rows
\cite{EPRINT:FenRiv25b}.

The PACS language distinguishes two classes of constraints. \emph{Parallel constraints} are enforced pointwise on
\(\Omega\); they are used for slot-local algebra such as linear relations, pointwise products, selector gating, and PRF
checkpoint constraints. \emph{Aggregated constraints} are enforced through \(\Omega\)-sum identities; they are used when
the encoding introduces a global coupling across packed coordinates. We keep this distinction at the proof-language level,
but in the remainder of the section we group constraints semantically rather than restating the PACS split every time.

\subsection{Recurring compilation devices}
\label{subsec:compilation-devices}
\label{subsec:abstract-compiled}
Two compilation patterns recur throughout both issuance and showing.

\paragraph{Carrier rows and decode bridges.}
When a row is known a priori to lie in a low-alphabet set, we do not carry it directly in the witness equations.
Instead, we commit a \emph{carrier row} whose values lie in a fixed public set, enforce carrier membership by a public
vanishing polynomial, and recover the rows that participate in the protocol equations through fixed public decode maps.
This is exactly the compression/decompression viewpoint used in SmallWood for low-alphabet lattice witnesses
\cite[Section~6]{EPRINT:FenRiv25b}. We therefore explain the device once here and then refer only to \emph{carrier
membership} and \emph{decode bridges} below. The exact carrier alphabets and decode maps for ARC-SPRUCE are recorded in
Appendix~\ref{app:smallwood}.

\paragraph{Replay-image rows and replay bridges.}
The showing proof is checked in a fixed public replay transform
\[
\mathcal F_{\mathrm{rep}} : \Rq \longrightarrow \mathcal T,
\]
partitioned into replay blocks
\[
\mathcal F_{\mathrm{rep}} = \bigl(\mathcal F_{\mathrm{rep},0},\ldots,\mathcal F_{\mathrm{rep},B_{\mathrm{rep}}-1}\bigr).
\]
The coefficient-domain statement lives on hidden source rows, but the verifier checks the rational-hash residual on exact
\emph{replay-image rows}, namely the blockwise images under \(\mathcal F_{\mathrm{rep}}\). The compiled relation
therefore contains explicit source-to-replay bridges. Once those bridges are proved, the replay residual is an exact
statement about the same hidden witness expressed in the replay basis. Section~\ref{subsec:statement-strength} later uses
this exactness to recover the coefficient-domain cleared identity.

\subsection{Issuance (pre-sign) compiled relation}
\label{subsec:smallwood-issuance}
\label{subsec:presign-compiled}
At the abstract level, issuance is governed by \(R_{\mathrm{Issue}}^{\mathrm{abs}}\) from
Section~\ref{sec:blind-signature}. The compiled SmallWood statement keeps the blind-signature target \(T\) public and
proves that it is consistent with one hidden commitment opening, the issuer randomness, and the centered randomness used
by the rational hash. As in Section~\ref{sec:blind-signature}, the compiled issuance relation is a cleared-denominator
statement rather than a direct quotient statement.

\paragraph{Committed rows.}
The issuance witness is organized into three semantic groups.
\begin{itemize}[leftmargin=1.25em]
    \item \emph{Compressed commitment and centering data:}
    \[
    C^M,\ C^{\mathrm{preRU}},\ C^{\mathrm{preR}},\ C^{\mathrm{ctr}},\ C^J.
    \]
    \item \emph{Decoded coefficient-domain rows:}
    \[
    M,\ K,\ R_0^U,\ R_1^U,\ R,\ R_0,\ R_1,\ J_0,\ J_1.
    \]
    \item \emph{Replay aliases for the public target relation:}
    \[
    \widehat M,\ \widehat K,\ \widehat R_0,\ \widehat R_1.
    \]
\end{itemize}
The exact row inventory and its proof-stack realization are recorded in Appendix~\ref{app:smallwood}; the main text
keeps only the semantic grouping.

\paragraph{Public inputs and lifts.}
The public issuance inputs are
\[
\mACom,\ B,\ \vecc,\ \vecr_0^{\Issuer},\ \vecr_1^{\Issuer},\ T.
\]
The verifier also derives the public lifts
\[
B_0^\Theta,\ B_1^\Theta,\ B_2^\Theta,\ B_3^\Theta,\ T^\Theta,
\]
where \(T^\Theta\) is the chosen public lift of the coefficient-domain target \(T\).

\paragraph{Constraint groups.}
The compiled issuance relation enforces five groups of constraints.
\begin{enumerate}[leftmargin=1.25em]
    \item \emph{Carrier membership and decode bridges.} The carrier rows lie in their designated low-alphabet sets, and
    the decoded rows are recovered from them by the fixed public decode maps.
    \item \emph{Commitment binding.} The decoded commitment rows satisfy
    \[
    \mACom\cdot [M\Vert K\Vert R_0^U\Vert R_1^U\Vert R]^\top = \vecc.
    \]
    \item \emph{Centering.} Writing \(\Delta=2\BoundMsg+1\), the centered randomness rows satisfy
    \[
    R_0 = R_0^U + \vecr_0^{\Issuer} - \Delta J_0,
    \qquad
    R_1 = R_1^U + \vecr_1^{\Issuer} - \Delta J_1.
    \]
    \item \emph{Packing and replay bridges.} The decoded rows \(M\) and \(K\) occupy complementary halves of the
    packing domain and together represent the abstract message \(\vecmu=\vecm\Vert \veck\). The four replay aliases
    \(\widehat M,\widehat K,\widehat R_0,\widehat R_1\) are the public replay images of \(M,K,R_0,R_1\).
    \item \emph{Replay-space cleared relation.} The public target \(T\), after lifting, satisfies
    \[
    (B_3^\Theta-\widehat R_1)\Had T^\Theta
    -
    \bigl(B_0^\Theta + B_1^\Theta\Had(\widehat M+\widehat K)+B_2^\Theta\Had \widehat R_0\bigr)
    =0.
    \]
\end{enumerate}

\paragraph{Statement proved.}
The compiled issuance proof therefore certifies that a single hidden commitment opening determines the decoded message and
randomness rows, that those rows satisfy the commitment and centering equations, that their replay aliases are exact, and
that the public target \(T\) satisfies the replay-space cleared relation with respect to those same hidden rows. This is
precisely the compiled issuance relation \(R_{\mathrm{Issue}}^{\mathrm{cmp}}\).

\subsection{Showing (post-sign) compiled relation}
\label{subsec:smallwood-showing}
\label{subsec:showing-compiled}
At the ARC layer, the abstract showing relation is the existence of a witness
\((\vecu,\vecm,\veck,r_0,r_1)\), with \(\vecmu=\vecm\Vert \veck\), such that
\[
\mA\vecu = h_{\vecmu,(r_0,r_1)}(B)
\qquad\text{and}\qquad
\prftag = \PRF(\veck,\nonce),
\]
together with the public coefficient-wise bounds on \(\vecm,\veck,r_0,r_1\) and the public shortness bound on
\(\vecu\). The compiled SmallWood statement realizes that witness in three layers.

First, the \emph{cert-side signature surface} proves shortness of the hidden signature witness and binds it to a hidden
coefficient-domain target row \(T\) satisfying \(T=\mA\vecu\). Second, the \emph{source rows}
\[
T,\ M,\ K,\ R_0,\ R_1,\ Z
\]
carry the coefficient-domain data from which the replay-space relation is derived; here \(Z\) is an inverse witness that
internalizes denominator admissibility. Third, the proof carries exact replay-image blocks for \(T\), \(M+K\),
\(R_0\), and \(R_1\), and checks the rational-hash residual in that replay basis.

\paragraph{Exact replay transform.}
Let
\[
\mathcal F_{\mathrm{rep}} : \Rq \longrightarrow \mathcal T
\]
denote the exact public replay transform, with block decomposition
\[
\mathcal F_{\mathrm{rep}} = \bigl(\mathcal F_{\mathrm{rep},0},\ldots,\mathcal F_{\mathrm{rep},B_{\mathrm{rep}}-1}\bigr).
\]
For every public hash polynomial \(B_i\in\Rq\), define the block lifts
\[
B_{i,b}^\Theta := \mathcal F_{\mathrm{rep},b}(B_i),
\qquad i\in\{0,1,2,3\},\quad b\in\{0,\ldots,B_{\mathrm{rep}}-1\}.
\]
These are the public coefficients used by the replay residual.

\paragraph{Committed rows.}
The committed showing witness is organized into five semantic groups.
\begin{itemize}[leftmargin=1.25em]
    \item \emph{Cert-side signature surface:} the signature limb rows \(L_{c,b,\ell}\), from which the cert-side
    signature surface and the coefficient-domain witness \(\vecu\) are reconstructed by the public collapse map of the
    shortness gadget.
    \item \emph{Compressed non-sign data:}
    \[
    C^M,\ C^{\mathrm{ctr}}.
    \]
    \item \emph{Coefficient-domain source rows:}
    \[
    T,\ M,\ K,\ R_0,\ R_1,\ Z.
    \]
    \item \emph{Replay-image block families:}
    \[
    \widehat T_0,\ldots,\widehat T_{B_{\mathrm{rep}}-1},
    \qquad
    \widehat m_0,\ldots,\widehat m_{B_{\mathrm{rep}}-1},
    \]
    \[
    \widehat R_{0,0},\ldots,\widehat R_{0,B_{\mathrm{rep}}-1},
    \qquad
    \widehat R_{1,0},\ldots,\widehat R_{1,B_{\mathrm{rep}}-1}.
    \]
    \item \emph{PRF companion rows.}
\end{itemize}
Again, the exact row inventory and PACS split are deferred to Appendix~\ref{app:smallwood}.

\paragraph{Constraint groups.}
The compiled showing relation enforces six groups of constraints.
\begin{enumerate}[leftmargin=1.25em]
    \item \emph{Cert-side signature shortness and target binding.} The limb rows satisfy the chosen shortness profile,
    the public collapse map reconstructs the cert-side signature surface, and the hidden target row \(T\) is bound to the
    same signature witness by
    \[
    T = \mA\vecu.
    \]
    \item \emph{Carrier membership, decode bridges, and packing.} The carrier rows \(C^M\) and
    \(C^{\mathrm{ctr}}\) lie in their designated alphabets; the fixed public decode maps recover \(M,K,R_0,R_1\);
    and \(M\) and \(K\) satisfy the same half-split message representation as in issuance.
    \item \emph{Source-to-replay bridges.} For every replay block \(b\),
    \[
    \widehat T_b = \mathcal F_{\mathrm{rep},b}(T),
    \qquad
    \widehat m_b = \mathcal F_{\mathrm{rep},b}(M+K),
    \]
    \[
    \widehat R_{0,b} = \mathcal F_{\mathrm{rep},b}(R_0),
    \qquad
    \widehat R_{1,b} = \mathcal F_{\mathrm{rep},b}(R_1).
    \]
    \item \emph{Blockwise replay residual.} For every replay block \(b\),
    \[
    (B_{3,b}^\Theta-\widehat R_{1,b})\Had \widehat T_b
    -
    \bigl(B_{0,b}^\Theta + B_{1,b}^\Theta\Had \widehat m_b + B_{2,b}^\Theta\Had \widehat R_{0,b}\bigr)
    =0.
    \]
    \item \emph{Inverse-witness constraint.} The source row \(Z\) internalizes admissibility by satisfying
    \[
    (B_3-R_1)\Had Z = 1.
    \]
    This source-side witness is what later upgrades the replay-space cleared identity to the abstract quotient relation.
    \item \emph{PRF companion constraints.} The companion rows are bound to the signed hidden key carried by \(K\),
    satisfy the checkpointed PRF equations, and bind the public pair \((\nonce,\prftag)\).
\end{enumerate}

\paragraph{Statement proved.}
The compiled showing proof therefore certifies that one and the same hidden credential witness supports four uses at
once: the cert-side signature witness is short and maps to the coefficient-domain target row \(T\); the source rows
\(T,M,K,R_0,R_1\) have exact replay images whose replay residual vanishes blockwise; the inverse witness \(Z\)
internalizes denominator admissibility inside the compiled statement; and the same signed hidden key \(K\)
is tied to the public tag by the PRF companion constraints. The abstract quotient relation is then recovered only through
the theorem suite of Section~\ref{subsec:statement-strength}.

\subsection{PRF companion constraints}
\label{subsec:prf-checkpointed}
\label{subsec:prf-constraints}
The public tag is tied to the signed hidden key by a companion PRF relation for the Poseidon2-like permutation from
Section~\ref{subsec:poseidon-prf}. At the level needed in the main body, this relation has three parts.
\begin{enumerate}[leftmargin=1.25em]
    \item \emph{Key binding.} Public selector constraints identify the signed key lanes inside the packed message rows
    and bind them to the PRF companion surface.
    \item \emph{Nonlinear checkpoints.} The proof certifies the selected S-box steps of the Poseidon2-like permutation,
    while the verifier replays the linear wiring between checkpoints from openings and public constants.
    \item \emph{Feed-forward and truncation.} The final state is combined with the input state and truncated so as to
    bind the public tag to the same hidden key and public nonce.
\end{enumerate}
In our concrete measurements we realize this companion relation with grouped checkpoints, but that grouping is an
instantiation choice rather than part of the abstract statement strength. The exact checkpoint schedule, row counts, and
instantiation-specific notes are deferred to Appendix~\ref{app:prf}.

\subsection{Coefficient-domain consequence and statement strength}
\label{subsec:statement-strength}
The completeness, knowledge-soundness, and zero-knowledge guarantees imported from SmallWood apply to the compiled PACS
relations stated above. In particular, the showing proof directly certifies the replay-space statement on the exact
replay-image blocks. Whenever later sections use a coefficient-domain consequence of that proof, they do so only through
the theorem suite below.

\begin{lemma}[Exact replay transform]\label{lem:replay-transform}
The public replay map
\[
\mathcal F_{\mathrm{rep}} : \Rq \longrightarrow \mathcal T
\]
is the exact transform isomorphism used by the replay basis. In particular, it is additive, multiplicative, and
injective.
\end{lemma}

\begin{proof}
Deferred to Appendix~\ref{app:smallwood}.
\end{proof}

\begin{lemma}[Coefficient-domain cleared consequence of the compiled showing relation]\label{lem:showing-to-cleared}
Assume the compiled showing relation of Section~\ref{subsec:showing-compiled}. Then the source rows satisfy
\[
B_3T-TR_1-B_0-B_1(M+K)-B_2R_0=0
\]
in \(\Rq\). Since the same compiled relation also enforces \(T=\mA\vecu\), it follows that
\[
B_3\mA\vecu-(\mA\vecu)R_1-B_0-B_1(M+K)-B_2R_0=0
\]
in \(\Rq\).
\end{lemma}

\begin{proof}
Deferred to Appendix~\ref{app:smallwood}.
\end{proof}

\begin{corollary}[Abstract rational-hash relation certified by the compiled statement]\label{cor:showing-to-abstract}
Assume the compiled showing relation of Section~\ref{subsec:showing-compiled}. Then the extracted witness satisfies
\[
(B_3-R_1)\Had Z = 1,
\qquad
T = Z\Had\bigl(B_0+B_1(M+K)+B_2R_0\bigr),
\]
and therefore
\[
T = h_{M+K,(R_0,R_1)}(B)
\qquad\text{and hence}\qquad
\mA\vecu = h_{M+K,(R_0,R_1)}(B).
\]
In particular, no external admissibility side condition is required beyond the witness certified by the proof itself.
\end{corollary}

\begin{proof}
The compiled showing relation already enforces \((B_3-R_1)\Had Z=1\), so \(B_3-R_1\in\Rq^\times\). By
Lemma~\ref{lem:showing-to-cleared},
\[
(B_3-R_1)\Had T-\bigl(B_0+B_1(M+K)+B_2R_0\bigr)=0.
\]
Multiplying by \(Z\) and using \((B_3-R_1)\Had Z=1\) gives
\[
T = Z\Had\bigl(B_0+B_1(M+K)+B_2R_0\bigr).
\]
Lemma~\ref{lem:hash-cleared-admissible} then yields
\[
T = h_{M+K,(R_0,R_1)}(B).
\]
Together with the cert-side bridge \(T=\mA\vecu\), this gives the final identity.
\end{proof}

\begin{corollary}[Consequence of an accepting post-sign proof]\label{cor:showing-proof-consequence}
Assume the post-sign NIZK is knowledge sound for the compiled showing relation. Then every accepting post-sign proof
extracts a witness \((\vecu,T,M,K,R_0,R_1,Z)\) satisfying both
\[
B_3\mA\vecu-(\mA\vecu)R_1-B_0-B_1(M+K)-B_2R_0=0
\]
and
\[
\mA\vecu = h_{M+K,(R_0,R_1)}(B)
\]
in \(\Rq\).
\end{corollary}

\begin{proof}
Knowledge soundness yields a witness satisfying the compiled showing relation. Lemma~\ref{lem:showing-to-cleared} gives
the cleared coefficient-domain identity, and Corollary~\ref{cor:showing-to-abstract} upgrades it to the abstract
quotient relation certified by the same witness.
\end{proof}

\begin{remark}[Statement strength]
The lemma above is the sole bridge from replay-space certification to the coefficient-domain cleared identity used later
in Section~\ref{sec:arc-construction}. The inverse witness \(Z\) then upgrades that cleared identity to the abstract
quotient relation inside the compiled statement itself. No converse implication from the coefficient-domain identities back
to the full replay-image relation is claimed.
\end{remark}
