\section{Blind Signature Construction}
\label{sec:blind-signature}

This section presents the vSIS-based blind signature that underlies ARC-SPRUCE. It combines the Ajtai commitment of
Section~\ref{subsec:commitments}, the trapdoor rational hash of Definition~\ref{def:rational-hash}, and the NIZK-ARK of
Definition~\ref{def:nizk-ark}. The signed message is denoted as $\vecmu$.
%\[
%  \vecm=\vecmu\Vert \veck,
%\]
%where \(\vecmu\) denotes the attribute payload and \(\veck\) is a holder-generated secret PRF key used later for rate
%limiting.

\subsubsection{Randomizing the rational-hash witness}
In the protocol, \(\Holder\) first commits to
\[
  \vecw=[\vecmu\Vert \vecr_0^{\Holder}\Vert \vecr_1^{\Holder}\Vert \bar\vecr]^\top,
\]
where \((\vecr_0^{\Holder},\vecr_1^{\Holder})\) are the holder contributions to the rational-hash witness and
\(\bar\vecr\) is fresh commitment randomness. To satisfy the commitment bounds, we require
\(\|\vecw\|_\infty\le \BoundMsg\).

The issuance process then uses a two-party randomness generation step: the issuer samples
\((\vecr_0^{\Issuer},\vecr_1^{\Issuer})\), and the joint witness is obtained coefficient-wise by computing
\[
  \vecr_0=\centerfunc(\vecr_0^{\Holder}+\vecr_0^{\Issuer}),\qquad
  \vecr_1=\centerfunc(\vecr_1^{\Holder}+\vecr_1^{\Issuer})
\]
which simply centers the output to the correct interval. Appendix~\ref{app:defs} describes this function in more detail.

\subsubsection{Blind Signature protocol}
\label{subsec:bs-protocol}
We assume \(\nizkscheme=(\ZKProve,\ZKVerify)\) is a NIZK for the relations below,
\(\ComScheme=(\ComSetup,\Commit,\ComVerify)\) is the Ajtai commitment scheme, and
\[
  \TDRH=(\Setup,\TrapGen,\Eval,\SampPre)
\]
is a trapdoor rational hash according to Definition~\ref{def:bbs-rational-hash}. The public setup will output the hash key
\(B\), while issuer key generation outputs the trapdoored signing matrix \(\mA\) as public verification key.
 We define the relations
\[
\relIssueBS:=\left\{ \left(  \begin{pmatrix}
	\ComPublicParam,\vecc,\\ 
    t, \vecr_0^{\Issuer},\vecr_1^{\Issuer}, \\
    \mA,B
\end{pmatrix},(\vecw=\begin{bmatrix}
\vecmu \\
\vecr_0^{\Holder}\\
 \vecr_1^{\Holder} \\
 \bar r
\end{bmatrix})\right) ~\bigg |~ \begin{matrix} \ComPublicParam=(\mACom,\BoundMsg)  \land  \\
\vecc = \mACom \vecw  \land \\
 ||\vecw||_{\infty} \leq \BoundMsg \land \\ 
\vecr_0= \centerfunc(\vecr_0^{\Holder}+\vecr_0^{\Issuer}) \land  \\
\vecr_1=\centerfunc(\vecr_1^{\Holder}+\vecr_1^{\Issuer}) \land \\
\vect = h_{\vecmu,(\vecr_0,\vecr_1)}(B) \end{matrix}  \right\}
\]
and
\[
\relSign :=\left\{ \left( \begin{pmatrix}
\mu, \mA,B, \\
\BoundMsg,\BoundSig
\end{pmatrix},(\vecw = \begin{bmatrix}
\vecr_0\\ \vecr_1 \\ \vecu
\end{bmatrix})\right) ~\bigg |~ \begin{matrix} 
  ||\vecr_0,\vecr_1||_{\infty} \leq \BoundMsg \land\\
  ||\vecu||_\infty \leq \BoundSig  \land \\
	\mA \vecu = h_{\vecmu,(\vecr_0,\vecr_1)}(B) \end{matrix}  \right\}
\]


Our Blind Signature scheme is then defined as follows:
	\begin{description}
		  \item[$\Setup(\SecParam)$:] ~
          \begin{enumerate}
          \item Run 
  \[
    (\mACom,\BoundMsg)\gets \ComScheme.\ComSetup(\SecParam)
  \]
  and
  \[
    (B,\mathcal{M},\mathcal{X},\delta,\BoundMsg,\BoundSig)\gets \TDRH.\Setup(\SecParam).
  \]
  
  \item Output $\PublicParamsBS=(\mACom,B,\mathcal{M},\mathcal{X},\delta,\BoundMsg,\BoundSig)$.
  	\end{enumerate}
        \item[$\IKeyGen()$:] ~
		\begin{enumerate}
			\item  Compute \((\mA,\trapdoor)\gets \TDRH.\TrapGen(\SecParam)\). 
			\item  Output $\vk=(\mA)$ and $\sk =(\trapdoor)$.
		\end{enumerate}
		\item[$\Issue$:] $\Issuer$ holds $\sk$ while $\Holder$ has $\mu,\vk$. 
        \begin{enumerate}
\item $\Holder$ samples \(\vecr_0^{\Holder},\vecr_0^{\Holder},\bar \vecr\) coefficient-wise in \([-\BoundMsg,\BoundMsg]\).
\item $\Holder$ computes \(\vecc\gets \mACom\cdot [\vecmu\Vert  \vecr_0^{\Holder}\Vert \vecr_0^{\Holder}\Vert \bar \vecr]^\top\) and sends \(\vecc\) to \(\Issuer\).
\item $\Issuer$ samples \(\vecr_0^{\Issuer},\vecr_1^{\Issuer}\) coefficient-wise in \([-\BoundMsg,\BoundMsg]\) and sends \((\vecr_0^{\Issuer},\vecr_1^{\Issuer})\) to \(\Holder\).
\item $\Holder$ sets \(\vecr_0 \gets \centerfunc(\vecr_0^{\Holder}+\vecr_0^{\Issuer})\) and \(\vecr_1 \gets \centerfunc(\vecr_0^{\Holder}+\vecr_1^{\Issuer})\).
\item\label{bs:step:issuancenizk} $\Holder$ computes \(\vect\gets h_{\vecmu,(\vecr_0,\vecr_1)}(B)\) and produces the
\emph{issuing} NIZK \(\nizkIssue\) using $\nizkscheme.\ZKProve$ proving knowledge of \((\vecmu,\vecr_0^{\Holder},\allowbreak \vecr_0^{\Holder},\bar \vecr)\) satisfying relation $\relIssueBS$.
\item $\Holder$ sends \((\vect,\nizkIssue)\) to \(\Issuer\).
\item $\Issuer$ verifies \(\nizkIssue\) for relation $\relIssueBS$ on $\vecc,\vect$ using $\nizkscheme.\ZKVerify$; if it accepts, sample \(\vecu \gets \TDRH.\SampPre(\trapdoor,\vect)\) and send \(\vecu\) to \(\Holder\). Otherwise abort.
\item $\Holder$ checks \(\mA \vecu = \vect\) and that \( || \vecu ||_\infty \leq \BoundSig  \). If not, then abort.
\item\label{bs:step:signingnizk} $\Holder$ computes a 
\emph{signing} NIZK \(\nizkSign\) using $\nizkscheme.\ZKProve$ proving knowledge of \((\vecu,\vecr_0,\vecr_1)\) for the relation $\relSign$.
\item Set $\sig:=(\nizkSign)$.
        \end{enumerate}
		\item[$\Verify(\vk,\mu,\sig)$:] For $\sig=(\pi)$ verify the relation $\relSign$ using $\nizkscheme.\ZKVerify$ and accept if the proof verifies, otherwise reject.
	\end{description}

%For ARC, the holder does not reveal \(\sig\) directly. Section~\ref{sec:arc-construction} instead proves the relation
%\(\relSign\) in zero knowledge while keeping \(\veck,\vecr_0,\vecr_1\) hidden and binding \(\veck\) to the PRF tag.

\subsubsection{Security}
\begin{proposition}[Correctness]
Assume correctness of $\nizkscheme,\TDRH$. Then the construction is correct according to Definition \ref{def:bs-correctness}.
\end{proposition}

\begin{proof}
Given the choice of $\vecr_0,\vecr_1$, $h_{\mu,(\vecr_0,\vecr_1)}(B)\neq \bot$ except with negligible probability.
Completeness of the pre-sign NIZK implies that $\Issuer$ accepts the proof $\nizkIssue$ for relation \(\relIssueBS\). By correctness of
\(\SampPre\), the returned \(\vecu\) satisfies \(\mA\vecu=\vect\) and has norm $\leq \BoundSig$ except with negligible
probability. The output \(\sig=(\vecu,\vecr_0,\vecr_1)\) therefore satisfies \(\relSign\) except with the negligible probability.
\end{proof}

\begin{proposition}[Blindness]
Assume that $\nizkscheme$ is zero-knowledge and $\ComScheme$ is hiding. Then the construction is blind according to Definition \ref{def:bs-blindness}.
\end{proposition}

\begin{proof}
    Let $\adversary$ be any adversary that wins   $\mathsf{Exp}^{\mathsf{sig\mbox{-}blind}}_{\mathsf{BSig},\Adv}(\lambda)$ with non-negligible probability. We construct the following sequence of hybrids:
    \begin{enumerate}
        \item Run the Blindness security game as in Definition \ref{def:bs-blindness}.
        \item Run the security game as above, but $\mathcal{C}$ creates the NIZKs in Step \ref{bs:step:issuancenizk} and \ref{bs:step:signingnizk} of $\Issue$ using the simulator of $\nizkscheme$. By assumption, this is indistinguishable from the previous step except with negligible probability.
        \item Run the same security game as above, but $\mathcal{C}$ now ignores $\mathcal{u},\mathcal{r}_0,\mathcal{r}_1$ in the simulation of Step \ref{bs:step:signingnizk} of $\Issue$. By assumption, this is indistinguishable from the previous step except with negligible probability.
        \item \cb{stuck here. how do we simulate $t$?} Next step: simulate $\vect$ based on some property of $h$.
        \item Finally: everything except $\vecc$ is independent of $\mu_b$ and therefore $b$. Thus, the attacker breaks the hiding property of $\ComScheme$ with loss factor $2$ by embedding a challenge in the first $\Issue$ query with $\Adv$ and committing to a random $\mu_i$ the second session. Whenever the queried commitment contains $\mu_i$ the attacker cannot win information-theoretically, and the other case is identical with the original security game.
    \end{enumerate}
\end{proof}


\cb{todo: add a proof for unforgeability.}


\begin{remark}[Security status of the blind protocol]\label{rem:blind-security-roadmap}
The non-blind hash-and-preimage signature layer underlying this protocol is justified by the DKLW25 reduction summarized
in Lemma~\ref{lem:vsis-unforgeability}. For the blind protocol itself, the only theorem-backed property proved in the
present draft is honest-party correctness. A proof of one-more unforgeability would still have to combine the
extractability of the pre-sign proof, the hiding of the Ajtai commitment, the algebraic correctness of the centering
step, and an interactive one-more hardness statement that genuinely matches the issuance oracle. A proof of blindness
would still have to combine the same commitment-hiding and proof zero-knowledge ingredients with a simulation argument
for the issuer view. Accordingly, the blind protocol is presented here as a construction with defined goals and an
explicit reduction roadmap, not as a layer for which blindness or one-more unforgeability has already been reduced.
\end{remark}

\begin{comment}
\begin{remark}[Security roadmap]
The non-blind hash-and-preimage signature layer underlying this protocol is justified by the DKLW25 reduction discussed
in Remark~\ref{rem:vsis-unforgeability}. For the blind protocol itself, the intended route is to combine straightline
extractability of the pre-sign proof with an interactive \(\mathsf{GenISIS}_f\)-style assumption for
\[
  f(B,\vecmu,(\vecr_0,\vecr_1))=h_{\vecmu,(\vecr_0,\vecr_1)}(B),
\]
while using statistical hiding of the Ajtai commitment and zero knowledge of the pre-sign proof in the blindness
argument. This explains why the construction targets one-more unforgeability and blindness, but we do not claim a
completed reduction for either property here.
\end{remark}
\end{comment}
