\section{Experimental Results}\label{sec:results}

\paragraph{Scope.}
We report end-to-end prover time, proof size, and soundness (in bits, via the composition in \S\ref{sec:final-soundness}).
All runs use the small-field variant with extension degree $\theta>1$; the opening degree $d_Q$ is as defined in Eq.~\eqref{eq:dQ}.
Mechanistic details of PACS/PIOP, DECS/LVCS, and the small-field compilation are recalled earlier; here we focus on the measured trade-offs.

\paragraph{Measurement grid.}
We sweep the main knobs that influence communication and soundness : packing $(n_{\text{cols}},\ell)$, point checks $\ell'$, masks $\rho$, extension degree $\theta$, and DECS window $\eta$. We report the resulting sizes, prover time (Time taken to build the NIZK Transcript), and bit security.

\begin{table}[h]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{r r r r r r r r r}
\toprule
\textbf{ProofKB} & \textbf{Time (s)} & \textbf{Bits} & \textbf{NCols} & $\ell$ & $\ell'$ & $\rho$ & $\theta$ & $\eta$\\
\midrule
\ \ 9.32 & 0.266 & 133.44 & 6 & 22 & 2 & 2 & 4 & 17 \\
10.07 & 0.228 & 146.93 & 4 & 24 & 2 & 2 & 4 & 17 \\
11.52 & 0.250 & 133.22 & 4 & 28 & 2 & 2 & 4 & 17 \\
\midrule[1.2pt]
14.06 & 0.630 & 198.01 & 4 & 34 & 8 & 5 & 2 & 26 \\
14.17 & 0.654 & 192.26 & 6 & 34 & 8 & 5 & 2 & 26 \\
14.24 & 0.670 & 198.48 & 4 & 34 & 8 & 6 & 2 & 26 \\
\bottomrule
\end{tabular}
\caption{Prover time, proof size, and achieved soundness across packing and PIOP knobs (small-field, $\theta>1$). Sizes exclude public parameters.}
\label{tab:results-grid}
\end{table}

\paragraph{Findings.}
We measure the results for two different regimes/soundness parameters goals :
First, a compact/low-latency band around $\lambda\!\geq\!128$ bits, obtained with $\theta=4$ and very few point checks ($\ell'=2$), yielding $9$–$12$\,KB proofs and $\approx 0.23$–$0.27$\,s proving.
Within this band, retuning $(n_{\text{cols}},\ell)$ shifts load between row openings and query payloads while keeping the opening degree governed by Eq.~\eqref{eq:dQ}, explaining the modest variation in size and bits.
Second, a high-security band at $\lambda\!\geq 192$ bits, reached with $\theta=2$, a higher $\ell'=8$, several masks ($\rho\in\{5,6\}$), and a wider DECS window, giving $\approx 14$\,KB proofs in $\approx 0.63$–$0.67$\,s.
The movement from $(\theta,\ell',\rho)=(4,2,2)$ to $(2,8,5\text{–}6)$ trades replication against per-check entropy exactly as predicted by the earlier calculus, without altering the underlying construction.

\paragraph{Guidance.}
For $\lambda\!\approx\!128$–$147$ bits, $(n_{\text{cols}},\ell,\ell',\rho,\theta,\eta)=(6,22,2,2,4,17)$ or $(4,24,2,2,4,17)$ delivers 9–10\,KB proofs with the fastest proving.
For $\lambda\!\approx\!192$–$198.5$ bits, $(4,34,8,5\text{–}6,2,26)$ attains $\approx 14$\,KB at sub-second proving.
Further knob interactions are as discussed earlier.
