\section{Gaussian Preimage Sampling}
\label{app:gaussian-sampler}

This appendix details the Gaussian preimage sampler used by the issuer to sign a
target \(t\in\Rq^n\) by producing a short preimage \(u\in\R^m\) such that
\(A u = t\) in \(\Rq^n\). Our instantiation follows the same vSIS trapdoor
setting used for the retained BB-tran target relation and relies on an NTRU
trapdoor generated via Antrag together with a hybrid two-plane sampler
\cite{EPRINT:DKLW25,EPRINT:ENSTW23}.

\subsection{The preimage sampling problem}
Given a public linear map \(A\in\Rq^{n\times m}\) and a target \(t\in\Rq^n\), the signer samples
\[
  u \;\gets\; \SampPre(\mathsf{td}_A,t)
  \qquad\text{such that}\qquad
  A u \equiv t \pmod q
\]
and \(u\) is short (according to a public bound \(\BoundSig\)). Equivalently, \(u\) lies in the coset lattice
\[
  \Lambda_{\perp}^{t}(A)\coloneqq \{\,x\in\R^{m} : A x \equiv t\ (\bmod\ q)\,\}.
\]
We require:
(i) correctness (\(Au=t\) and the norm test fails only with negligible probability),
(ii) (approx.) Gaussianity of \(u\) over the coset (statistical hiding of the trapdoor),
and (iii) a tight tail bound that supports efficient ZK range/norm checks in the post-sign proof.

\subsection{NTRU trapdoor form and quality}
\label{subsec:ntru-trapdoor}
We work with the rank-2 NTRU module over the cyclotomic ring \(\R=\Z[X]/(X^N+1)\) and its quotient \(\Rq\). An NTRU
public key has the form \(h=g f^{-1}\bmod q\) for secret \(f,g\in\R\). The corresponding module is
\[
  \mathsf{L}_{\mathsf{NTRU}}(h)
  \;=\;
  \{(u,v)\in \R^2 : u h - v \equiv 0 \ (\bmod q)\}.
\]
A trapdoor basis of \(\mathsf{L}_{\mathsf{NTRU}}(h)\) is
\[
  B_{f,g}
  \;=\;
  \begin{pmatrix}
    f & F\\
    g & G
  \end{pmatrix},
  \qquad\text{with}\qquad fG - gF \;=\; q,
\]
whose columns are short and satisfy \(g/f \equiv G/F \equiv h \pmod q\). Following \cite{EPRINT:ENSTW23}, we
measure trapdoor quality via per-slot energies under the canonical embeddings \(\varphi_i\), requiring a uniform window
around \(q\). Concretely, for a quality parameter \(\alpha>1\) we target
\[
  \frac{q}{\alpha^2} \ \le\ |\varphi_i(f)|^2 + |\varphi_i(g)|^2 \ \le\ \alpha^2 q
  \qquad\text{for all slots \(i\)}.
\]
Smaller \(\alpha\) corresponds to tighter trapdoors and, for fixed \(N,q\), to shorter signatures for the same security.

\subsection{Sampler definition and tuning}
\label{subsec:sampler-tuning}
Our sampler is a ring-based hybrid two-plane sampler in the evaluation domain. The sampler’s main tuning parameters are:
\begin{itemize}[leftmargin=1.25em]
  \item modulus \(q\) and ring degree \(N\),
  \item trapdoor quality \(\alpha\),
  \item acceptance radius \(R_{\mathrm{acc}}\) (controls rejections and \(\ell_\infty/\ell_2\) tails),
  \item per-slot widths \(\sigma_k[i]\) (two planes \(k\in\{1,2\}\)).
\end{itemize}

\paragraph{Per-slot calibration.}
Let \(\widetilde{b}_k[i]\) denote the per-slot Gram--Schmidt lengths for plane \(k\) at slot \(i\). A standard
calibration equalizes acceptance probability across slots:
\[
  \sigma_k[i]
  \;=\;
  \sqrt{\ \frac{\alpha^2 q\,R_{\mathrm{acc}}^2}{\|\widetilde{b}_k[i]\|^2}\ -\ R_{\mathrm{acc}}^2\ }
  \qquad(k\in\{1,2\}).
\]
This prevents weak slots and yields consistent output variance.

\paragraph{Hiding threshold (smoothing).}
To achieve statistical hiding, we enforce a floor \(\sigma_{\min}\) such that \(\sigma_k[i]\ge \sigma_{\min}\) for all
\(k,i\), where \(\sigma_{\min}\) exceeds the smoothing parameter of the relevant lattice cosets. In practice, we apply a
global scale factor to raise all \(\sigma_k[i]\) above the theoretical floor with slack.

\subsection{Annulus sampling (Antrag key generation)}
\label{subsec:antrag}
Antrag replaces trial-and-error trapdoor generation with direct annulus sampling in the Fourier domain
\cite{EPRINT:ENSTW23}. For each conjugate pair (there are \(N/2\) independent slots), the key generator samples
\((|\varphi_i(f)|,|\varphi_i(g)|)\) uniformly in an annulus arc \(A^+(r,R)\) with
\[
  \sqrt{q}/\alpha \ <\ r \ <\ R \ <\ \alpha\sqrt{q},
\]
chooses random phases, inverse-embeds to the coefficient domain, and rounds to obtain \((f,g)\in\R^2\). By selecting a
``middle'' annulus window (see \cite{EPRINT:ENSTW23}) one ensures that the rounded trapdoor satisfies the desired
\(\alpha\)-window with high probability and with modest repetition.

\subsection{Hybrid two-plane sampler (details)}
\label{subsec:hybrid-sampler}
We sketch the two-plane hybrid sampler in the notation of \cite{EPRINT:ENSTW23}. Let \(\mathsf{td}_A\) encode an
NTRU trapdoor for \(A\) and let \(t\in\Rq^n\) be the target. Write \(\langle\cdot\rangle_q\) for signed coefficient lift
and define \(\mathrm{center}_q\) as coefficient-wise centering into \((-\frac{q}{2},\frac{q}{2}]\).

\begin{algorithm}[H]
\caption{\(\SampPre(\mathsf{td}_A,t)\): two-plane hybrid sampler (sketch)}
\label{alg:samppre}
\begin{algorithmic}[1]
\State Lift \(t\) to coefficients and set \(c \gets \mathrm{center}_q(t)\in(-\frac{q}{2},\frac{q}{2}]^n\).
\State Using \(\mathsf{td}_A\), compute per-slot widths \(\sigma_k[i]\) (two planes) calibrated to trapdoor quality.
\Repeat
  \State Sample slot-wise Gaussian pairs on the two planes, reconstruct a coefficient-domain candidate \(u\).
  \State Accept iff the norm predicate holds for \(u\) (e.g., \(\ell_2\) and/or \(\ell_\infty\) bound).
\Until{accepted}
\State \Return \(u\).
\end{algorithmic}
\end{algorithm}

\paragraph{Public relations.}
Downstream verification and proofs use only the public relation \(A u=t\) and shortness of \(u\) (bounded by \(\BoundSig\)),
checked by the holder on receipt and enforced by the issuer’s rejection sampling. The post-sign NIZK then proves
knowledge of such a short \(u\) without revealing it.
