\section{SmallWood Programming Model}
\label{sec:smallwood-model}

This section describes how the current ARC-SPRUCE issuance and showing
statements are compiled into SmallWood constraints. The proof-system internals
(DECS/LVCS/PCS/PIOP and Fiat--Shamir compilation) are deferred to
Appendix~\ref{app:smallwood}; here we fix the witness families and constraint
families that the implementation actually proves.

\subsection{What SmallWood provides (formal interface)}
Fix a witness-support domain
\(\Omega=\{\omega_0,\dots,\omega_{s-1}\}\subset\Fq\) of size \(s\), a
disjoint set of tail points \(\Omega'\subset\Fq\setminus\Omega\), and an
opening set \(E'\subset\Fq\setminus\Omega\) chosen by the verifier through
Fiat--Shamir. A witness is arranged as a matrix \(w\in\Fq^{n\times s}\), with
one committed polynomial \(P_i(X)\in\Fq[X]\) per row, such that
\(P_i(\omega_k)=w_{i,k}\) for all \(\omega_k\in\Omega\) and \(P_i\) takes
random values on \(\Omega'\) (HVZK tails). SmallWood commits to the full row
family and then replays constraint residuals from openings at \(E'\).

\paragraph{Parallel vs. aggregated PACS families.}
SmallWood's PACS language distinguishes:
\begin{itemize}[leftmargin=1.25em]
  \item \emph{parallel families}, enforced pointwise on \(\Omega\), and
  \item \emph{aggregated families}, enforced through the \(\Omega\)-sum test
  \(\sum_{\omega\in\Omega} F'(\omega)=0\).
\end{itemize}
Parallel families are used for slot-local algebra: carrier membership, decode
bridges, linear commitment and centering identities, replay residuals, packing,
and PRF checkpoint constraints. Aggregated families are used exactly where the
current implementation has a global linear map across packed coordinates,
namely the transform bridges from explicit-domain source rows to replay-facing
transform aliases.

\paragraph{Replay-facing aliases and Eq.(4) honesty.}
The current implementation uses explicit-domain committed polynomials for all
witness rows, but it also commits \emph{transform-domain aliases} whenever the
verifier must replay a quotient-ring relation from row openings. The reason is
mathematical rather than implementation-specific: a coefficient-domain identity
in \(\Fq[X]/(X^N+1)\) is generally \emph{not} preserved by naive scalar
evaluation of coefficient representatives at arbitrary points in \(E'\).
Therefore, whenever replay requires the verifier to recover ring-multiplication
semantics, the implementation commits explicit transform-domain aliases and
checks the replay relation in that basis.

\subsection{Constraint compilation recipe}
Given a ring statement, the current ARC compilation follows five steps:
\begin{enumerate}[leftmargin=1.25em]
  \item \textbf{Choose the committed witness surface.}
  Commit explicit-domain witness rows for the low-alphabet carriers, any
  decoded aliases that must replay linearly at \(E'\), and any replay-facing
  transform aliases required for quotient-ring relations.
  \item \textbf{Fix packing on \(\Omega\).}
  Use coefficient packing: each coordinate of \(\Omega\) represents one packed
  coefficient slot. Some logical surfaces, such as PRF companion rows, are
  packed even though they are conceptually column-constant.
  \item \textbf{Lift public rows into the replay basis.}
  Public hash rows and public signature-map rows are converted into
  theta-lifted explicit-domain polynomials, denoted \(B^\Theta\),
  \(T^\Theta\), and \(A^\Theta\), whose values on \(\Omega\) are the NTT-head
  values used by replay.
  \item \textbf{Split into parallel and aggregated families.}
  Parallel families enforce slot-local relations on committed rows or decoded
  virtual rows. Aggregated families enforce the global linear transform map
  from source rows to replay aliases.
  \item \textbf{Provide formal coefficient polynomials.}
  In explicit-domain mode the verifier replays polynomial identities at
  \(E'\), so the implementation supplies formal coefficient overrides for both
  parallel and aggregated families. This prevents the usual
  interpolate-then-multiply mismatch between pointwise \(\Omega\)-products and
  the actual committed explicit-domain polynomials.
\end{enumerate}

\subsection{Issuance (pre-sign) constraints}
\label{subsec:smallwood-issuance}
We rewrite the issuance relation of
Section~\ref{subsec:issuance-protocol} as a SmallWood statement whose public
target \(\vect\) remains public, with \(T\) denoting its coefficient-domain
representative inside the replay basis, and whose replay-safe hash check is
carried out on transform-domain aliases.

\paragraph{Committed witness rows.}
The current pre-sign witness surface is committed in the following order:
\[
  C^M,\ C^{\mathrm{preRU}},\ C^{\mathrm{preR}},\ C^{\mathrm{ctr}},\ C^J,
\]
\[
  M,\ K,\ R_U^0,\ R_U^1,\ R,\ R_0,\ R_1,\ J_0,\ J_1,
\]
\[
  \widehat M,\ \widehat K,\ \widehat R_0,\ \widehat R_1.
\]
The first five rows are low-alphabet carriers. The next nine rows are explicit
decoded aliases. The final four rows are the replay-facing transform aliases
needed only for the hash relation.

\paragraph{Carrier families.}
The message carrier \(C^M\) uses the same sparse packed codec as showing:
\[
S_M^{\mathrm{packed}}
=
\{(a,0):a\in[-\BoundMsg,\BoundMsg]\}
\cup
\{(0,a):a\in[-\BoundMsg,\BoundMsg]\},
\]
with \((0,0)\) deduplicated, contiguous code set \(\{0,\dots,4\BoundMsg\}\),
and membership degree \(4\BoundMsg\). The other issuance carriers use the
generic full pair codec
\[
  c=(x_0+B)+(2B+1)(x_1+B),
\]
with the appropriate bound for each family; in particular, \(C^J\) is a bound-1
pair carrier for \((J_0,J_1)\), and \(C^{\mathrm{preR}}\) stores
\((R,0)\), with only the first decoded coordinate used later.

\paragraph{Canonical decoded aliases.}
The decoded alias rows are not copied directly from the holder's raw witness.
Instead, the prover first commits the carrier rows, then composes the public
decode polynomials with those committed carrier polynomials, and commits the
resulting decoded aliases. Concretely,
\[
  (M,K)=\mathrm{Dec}_M(C^M),
\]
\[
  (R_U^0,R_U^1)=\mathrm{Dec}_{\mathrm{preRU}}(C^{\mathrm{preRU}}),\qquad
  R=\mathrm{Dec}^{(1)}_{\mathrm{preR}}(C^{\mathrm{preR}}),
\]
\[
  (R_0,R_1)=\mathrm{Dec}_{\mathrm{ctr}}(C^{\mathrm{ctr}}),\qquad
  (J_0,J_1)=\mathrm{Dec}_J(C^J).
\]
This matters because the verifier replays from committed row openings at
\(E'\): the alias rows must be the exact decode images of the committed
carriers.

\paragraph{Public inputs and lifted public rows.}
The public issuance inputs are
\[
  \mACom,\ B,\ \vecc,\ \vecr_0^{\Issuer},\ \vecr_1^{\Issuer},\ T.
\]
Here \(T\) denotes the coefficient-domain representative of the public blind
signature target \(\vect\) from Section~\ref{subsec:issuance-protocol}. The
current implementation also derives the public theta-lifts
\(B_0^\Theta,B_1^\Theta,B_2^\Theta,B_3^\Theta\) and \(T^\Theta\), where
\(T^\Theta\) is obtained from the public coefficient-domain target \(T\) by the
same NTT-head lift used elsewhere in the transform bridge.

\paragraph{Parallel issuance families.}
Let \(\Delta=2\BoundMsg+1\). The current pre-sign proof enforces the
following parallel families:
\begin{enumerate}[leftmargin=1.25em]
  \item \textbf{Carrier membership:}
  \[
    P_M(C^M)=0,\quad P_{\mathrm{preRU}}(C^{\mathrm{preRU}})=0,\quad
    P_{\mathrm{preR}}(C^{\mathrm{preR}})=0,\quad
    P_{\mathrm{ctr}}(C^{\mathrm{ctr}})=0,\quad
    P_J(C^J)=0.
  \]
  \item \textbf{Carrier-to-alias bridges:}
  \[
    M-\mathrm{Dec}_M^{(1)}(C^M)=0,\quad K-\mathrm{Dec}_M^{(2)}(C^M)=0,
  \]
  \[
    R_U^0-\mathrm{Dec}_{\mathrm{preRU}}^{(1)}(C^{\mathrm{preRU}})=0,\quad
    R_U^1-\mathrm{Dec}_{\mathrm{preRU}}^{(2)}(C^{\mathrm{preRU}})=0,
  \]
  \[
    R-\mathrm{Dec}_{\mathrm{preR}}^{(1)}(C^{\mathrm{preR}})=0,
  \]
  \[
    R_0-\mathrm{Dec}_{\mathrm{ctr}}^{(1)}(C^{\mathrm{ctr}})=0,\quad
    R_1-\mathrm{Dec}_{\mathrm{ctr}}^{(2)}(C^{\mathrm{ctr}})=0,
  \]
  \[
    J_0-\mathrm{Dec}_J^{(1)}(C^J)=0,\quad J_1-\mathrm{Dec}_J^{(2)}(C^J)=0.
  \]
  \item \textbf{Commitment:}
  \[
    \mACom\cdot[M\Vert K\Vert R_U^0\Vert R_U^1\Vert R]^\top=\vecc.
  \]
  \item \textbf{Centering:}
  \[
    R_0 = R_U^0 + \vecr_0^{\Issuer} - \Delta J_0,
    \qquad
    R_1 = R_U^1 + \vecr_1^{\Issuer} - \Delta J_1.
  \]
  \item \textbf{Packing:}
  \(M\) is constrained to the lower half of \(\Omega\), and \(K\) to the
  upper half, exactly as in the packed-message representation of
  Section~\ref{sec:arc-construction}.
  \item \textbf{Transform-domain public-target hash:}
  \[
    (B_3^\Theta-\widehat R_1)\,T^\Theta
    -\bigl(B_0^\Theta + B_1^\Theta(\widehat M+\widehat K)
    + B_2^\Theta\widehat R_0\bigr)=0.
  \]
\end{enumerate}

\paragraph{Aggregated issuance families.}
The current pre-sign statement has four aggregated families, namely the
non-sign transform bridges
\[
  M\rightarrow \widehat M,\qquad K\rightarrow \widehat K,
\]
\[
  R_0\rightarrow \widehat R_0,\qquad R_1\rightarrow \widehat R_1.
\]
No signature-side bridge is needed in issuance, and there is no committed
\(\widehat T\) witness row because the target remains public.

\paragraph{Why public issuance still uses hats.}
The commitment and centering equations are linear in the decoded aliases and
therefore replay-clean in that coefficient basis. The rational-hash equation is
not: replaying it from single-point openings of coefficient rows at arbitrary
points in \(E'\) does not preserve the quotient-ring multiplication used by the
hash. The current issuance design therefore mirrors the showing proof only for
the hash-facing rows: it keeps \(T\) public, derives the public lift
\(T^\Theta\), commits the four minimal non-sign hats, and checks the hash
relation in that transform basis.

\paragraph{Exact pre-sign statement now proved.}
The current issuance proof asserts the existence of committed carriers,
committed decoded aliases, and committed non-sign hats such that:
\begin{enumerate}[leftmargin=1.25em]
  \item each carrier lies in its low-alphabet carrier set,
  \item each decoded alias is the public decode image of its carrier,
  \item the decoded aliases satisfy commitment, centering, and packing,
  \item the hats are the exact transform images of \(M,K,R_0,R_1\), and
  \item the public target \(T\), after public theta-lift, satisfies the
  transform-domain hash equation with those hats.
\end{enumerate}
This is the minimal committed replay surface that makes the current
implementation honest under SmallWood replay while keeping the ARC issuance
target public.

\subsection{Showing (post-sign) constraints}
\label{subsec:smallwood-showing}
The showing proof rewrites the ARC presentation statement of
Section~\ref{subsec:showing-protocol} into a transform-bridge SmallWood
instance. The current statement is substantially smaller than earlier versions:
only the theorem-essential replay row \(\widehat T_0\) is committed on the
signature side, and the message transform aliases are deduplicated into one row
\(\widehat m\).

\paragraph{Fixed public algebra and transform map.}
Let \(A^\Theta\) denote the theta-lifted public signature map and
\(B_0^\Theta,B_1^\Theta,B_2^\Theta,B_3^\Theta\) the theta-lifted public replay
rows derived from the NTT heads of the corresponding public polynomials. The
transform-domain aliases are related to their explicit-domain source rows by one
exact public linear map \(\mathcal F\), implemented through a bridge matrix
\(H\) derived from the NTT matrix itself:
\[
  H_{t,k}=\mathrm{NTT}(e_k)_t,
\]
where \(e_k\) is the \(k\)-th coefficient basis vector. Thus \(H\) is not a
heuristic root-power map: it is the exact public linear transform matching the
implementation's NTT ordering.

\paragraph{Committed showing witness rows.}
The current showing witness surface consists of:
\begin{enumerate}[leftmargin=1.25em]
  \item \textbf{Cert-side signature limb rows}
  \(L_{c,b,\ell}\), used by the shortness gadget.
  \item \textbf{Carrier rows}
  \(C^M\) and \(C^{\mathrm{ctr}}\).
  \item \textbf{Replay-facing transform aliases}
  \(\widehat T_0,\widehat m,\widehat R_0,\widehat R_1\), where
  \(\widehat m=\mathcal F(M+K)\).
  \item \textbf{PRF companion rows} for the shipped checkpointed PRF path.
\end{enumerate}

\paragraph{What is no longer committed.}
The current implementation does \emph{not} commit any of the following older
surfaces:
\begin{itemize}[leftmargin=1.25em]
  \item packed signature source rows \(\widetilde S\),
  \item intermediate signature hats \(\widehat S\),
  \item semantic signature rows \(U\),
  \item semantic witness target rows \(T\),
  \item separate message hats \(\widehat M,\widehat K\).
\end{itemize}
Instead, \(\widetilde S\) is reconstructed virtually from the limb rows,
\(\widehat S\) is only a conceptual intermediate linear image, and the only
committed signature replay row is \(\widehat T_0\).

\paragraph{Virtual showing rows.}
The decoded non-sign rows remain virtual:
\[
  (M,K)=\mathrm{Dec}_M(C^M),\qquad
  (R_0,R_1)=\mathrm{Dec}_{\mathrm{ctr}}(C^{\mathrm{ctr}}).
\]
The virtual packed signature source is reconstructed linearly from the limb
surface as
\[
  \widetilde S_{c,b}=\sum_{\ell} r^\ell L_{c,b,\ell}.
\]
The intermediate signature hats are also virtual: they are the linear image of
\(\widetilde S\) under the same transform map, but they are not committed in
the final statement.

\paragraph{Parallel showing families.}
The current post-sign proof enforces the following parallel families:
\begin{enumerate}[leftmargin=1.25em]
  \item \textbf{Signature digit membership:}
  the limb rows satisfy the signed low-alphabet digit constraints of the chosen
  shortness profile.
  \item \textbf{Replay residual:}
  \[
    (B_3^\Theta-\widehat R_1)\widehat T_0
    -\bigl(B_0^\Theta + B_1^\Theta\widehat m + B_2^\Theta\widehat R_0\bigr)=0.
  \]
  \item \textbf{Packing:}
  the decoded virtual rows \(M,K\) satisfy the same half-split message
  representation as in issuance.
  \item \textbf{Carrier membership:}
  \(P_M(C^M)=0\) for the sparse packed-message carrier and
  \(P_{\mathrm{ctr}}(C^{\mathrm{ctr}})=0\) for the centered full-pair carrier.
  \item \textbf{PRF key binding and nonlinear constraints:}
  the packed companion rows are bound to decoded \(K\) lanes, satisfy the
  grouped S-box/checkpoint equations, and bind the public tag after the
  feed-forward and truncation step.
\end{enumerate}

\paragraph{Aggregated showing families.}
The current post-sign statement has three classes of aggregated families:
\begin{enumerate}[leftmargin=1.25em]
  \item \textbf{Direct limb-to-\(\widehat T_0\) bridge.}
  For each local coordinate \(j\), one aggregated family proves that the
  committed replay row \(\widehat T_0(\omega_j)\) is the exact public linear
  image of the limb surface under the combined signature map and transform map.
  This is the final replacement for both the committed
  \(\widetilde S\) layer and the committed \(\widehat S\) layer.
  \item \textbf{Non-sign transform bridges.}
  The proof enforces
  \[
    (M+K)\rightarrow \widehat m,
    \qquad
    R_0\rightarrow \widehat R_0,
    \qquad
    R_1\rightarrow \widehat R_1.
  \]
  \item \textbf{PRF constancy for unpacked PRF rows only.}
  This family is part of the general model but is empty in the shipped packed
  companion path.
\end{enumerate}

\paragraph{Exact post-sign statement now proved.}
The current showing proof asserts the existence of committed limb rows,
committed carriers, committed replay-facing transform aliases
\(\widehat T_0,\widehat m,\widehat R_0,\widehat R_1\), and PRF witness
rows such that:
\begin{enumerate}[leftmargin=1.25em]
  \item the cert-side signature is short via the limb decomposition,
  \item \(\widehat T_0\) is the direct public transform/image of that short
  cert-side surface,
  \item \(\widehat m,\widehat R_0,\widehat R_1\) are the transform
  images of the decoded non-sign rows,
  \item the replay residual vanishes, and
  \item the PRF rows bind the public tag to the signed hidden key and public
  nonce.
\end{enumerate}
Because \(\mathcal F\) is public and invertible, this is equivalent to the
coefficient-domain replay claim
\[
  B_3T - T\star R_1 - B_0 - B_1(M+K) - B_2R_0 = 0,
\]
with \(T\) certified as the cert-side signature image. The signature replay
surface has therefore already been reduced to the theorem-essential subset.

\subsection{Poseidon PRF constraints with checkpoints}
\label{subsec:prf-checkpointed}
This subsection records the logical PRF constraints used inside the current
showing statement. The shipped implementation carries them through packed
companion rows rather than through one explicit row per logical lane, but the
mathematical content is the same.

\paragraph{Logical PRF witness.}
Conceptually the PRF witness contains hidden key lanes and checkpointed
nonlinear outputs. In the shipped packed-companion path these logical values are
serialized into packed companion rows, but the verifier still replays the same
logical constraints from their opened evaluations.

\paragraph{Key binding.}
For each key lane, a public selector on \(\Omega\) binds the packed companion
value to the decoded packed-key row \(K\) at the designated coordinate. This is
the mechanism that ties the hidden PRF key to the signed message component
\(\veck\).

\paragraph{Checkpointed nonlinear constraints.}
The verifier recomputes the linear wiring between checkpoints and enforces the
grouped S-box equations at the committed checkpoints. These are parallel PACS
families. The grouping parameter controls the effective degree, but under the
current shipped parameters this PRF degree remains below the signature
shortness degree and does not dominate \(d_Q\).

\paragraph{Tag binding.}
The verifier reconstructs the final PRF state, applies the feed-forward with
the initial state, truncates to the public output lanes, and enforces equality
with the public tag. This is the public rate-limiting handle used by the ARC
showing protocol.

\subsection{Where details are deferred}
Appendix~\ref{app:smallwood} records the SmallWood proof stack itself:
DECS/LVCS/PCS/PIOP, Fiat--Shamir, and the exact replay checks. The Gaussian
trapdoor sampler remains in Appendix~\ref{app:gaussian-sampler}. The current
PRF algorithm and its checkpoint schedule remain tied to
Section~\ref{subsec:poseidon-prf} and Appendix~\ref{app:prf}. This section only
fixes the statement layer: which witness rows are committed, which rows are
virtual, and how the current implementation splits those relations into
parallel and aggregated SmallWood families.
