\section{Gaussian Preimage Sampling}
\label{app:gaussian-sampler}

This appendix describes the Gaussian preimage-sampling interface used by the issuer to sign a target
\(t\in\Rq^n\) by producing a short preimage \(u\in\R^m\) such that \(A u = t\) in \(\Rq^n\).  The security
import in Section~\ref{subsec:prelim-signatures} requires the admissible trapdoor-suite interface of
Definition~\ref{def:trapdoor-suite}.  The concrete implementation candidate described here follows the
vSIS--BB-tran setting~\cite{EPRINT:DKLW25} and uses an NTRU trapdoor generated via Antrag together with
a hybrid two-plane sampler~\cite{EPRINT:ENSTW23}.  Antrag is used here as a trapdoor-generation and
quality-tuning source, not as a standalone proof of the full DKLW admissible-suite interface.

\subsection{The preimage sampling problem}
Given a public linear map \(A\in\Rq^{n\times m}\) and a target \(t\in\Rq^n\), the signer samples
\[
  u \;\gets\; \SampPre(\mathsf{td}_A,t)
  \qquad\text{such that}\qquad
  A u \equiv t \pmod q
\]
and \(u\) is short (according to a public bound \(\BoundSig\)). Equivalently, \(u\) lies in the coset lattice
\[
  \Lambda_{\perp}^{t}(A)\coloneqq \{\,x\in\R^{m} : A x \equiv t\ (\bmod\ q)\,\}.
\]
For compatibility with the DKLW import, the sampler layer must provide:
(i) correctness (\(Au=t\) and the norm test fails only with negligible probability),
(ii) a preimage distribution close enough to the required lattice-coset Gaussian or an explicitly assumed
substitute distributional guarantee,
and (iii) a tail bound that justifies the public verification bound \(\BoundSig\) in the coefficient
\(\ell_\infty\)-norm used by the ARC relations.

\subsection{NTRU trapdoor form and quality}
\label{subsec:ntru-trapdoor}
We work with the rank-2 NTRU module over the cyclotomic ring \(\R=\Z[X]/(X^N+1)\) and its quotient \(\Rq\). An NTRU
public key has the form \(h=g f^{-1}\bmod q\) for secret \(f,g\in\R\). The corresponding module is
\[
  \mathsf{L}_{\mathsf{NTRU}}(h)
  \;=\;
  \{(u,v)\in \R^2 : u h - v \equiv 0 \ (\bmod q)\}.
\]
A trapdoor basis of \(\mathsf{L}_{\mathsf{NTRU}}(h)\) is
\[
  B_{f,g}
  \;=\;
  \begin{pmatrix}
    f & F\\
    g & G
  \end{pmatrix},
  \qquad\text{with}\qquad fG - gF \;=\; q,
\]
whose columns are short and satisfy \(g/f \equiv G/F \equiv h \pmod q\). Following \cite{EPRINT:ENSTW23}, we
measure trapdoor quality via per-slot energies under the canonical embeddings \(\varphi_i\), requiring a uniform window
around \(q\). Concretely, for a quality parameter \(\alpha>1\) we target
\[
  \frac{q}{\alpha^2} \ \le\ |\varphi_i(f)|^2 + |\varphi_i(g)|^2 \ \le\ \alpha^2 q
  \qquad\text{for all slots \(i\)}.
\]
Smaller \(\alpha\) corresponds to tighter trapdoors and, for fixed \(N,q\), to shorter signatures for the same security.

\subsection{Sampler definition and tuning}
\label{subsec:sampler-tuning}
Our candidate sampler is a ring-based hybrid two-plane sampler in the evaluation domain.  The sampler’s main
tuning parameters are:
\begin{itemize}[leftmargin=1.25em]
  \item modulus \(q\) and ring degree \(N\),
  \item trapdoor quality \(\alpha\),
  \item acceptance radius \(R_{\mathrm{acc}}\) controlling rejection and norm tails,
  \item per-slot widths \(\sigma_k[i]\) for the two planes \(k\in\{1,2\}\).
\end{itemize}

The concrete calibration formulas are implementation/tuning rules for the candidate sampler.  The paper's
signature-layer theorem uses them only through the admissible-suite properties in
Definition~\ref{def:trapdoor-suite}: correctness, the required distributional hiding guarantee, and a tail bound
implying \(\|u\|_\infty\le \BoundSig\) except with negligible probability.

\paragraph{Per-slot calibration.}
Let \(\widetilde{b}_k[i]\) denote the per-slot Gram--Schmidt lengths for plane \(k\) at slot \(i\). A standard
calibration equalizes acceptance probability across slots:
\[
  \sigma_k[i]
  \;=\;
  \sqrt{\ \frac{\alpha^2 q\,R_{\mathrm{acc}}^2}{\|\widetilde{b}_k[i]\|^2}\ -\ R_{\mathrm{acc}}^2\ }
  \qquad(k\in\{1,2\}).
\]
This prevents weak slots and yields consistent output variance.

\paragraph{Smoothing threshold.}
To obtain the sampler distributional guarantees required by the trapdoor interface, we enforce a floor \(\sigma_{\min}\) such that \(\sigma_k[i]\ge \sigma_{\min}\) for all
\(k,i\), where \(\sigma_{\min}\) exceeds the smoothing parameter of the relevant lattice cosets. In practice, we apply a
global scale factor to raise all \(\sigma_k[i]\) above the theoretical floor with slack.

\subsection{Annulus sampling (Antrag key generation)}
\label{subsec:antrag}
Antrag replaces trial-and-error trapdoor generation with direct annulus sampling in the Fourier domain
\cite{EPRINT:ENSTW23}. For each conjugate pair (there are \(N/2\) independent slots), the key generator samples
\((|\varphi_i(f)|,|\varphi_i(g)|)\) uniformly in an annulus arc \(A^+(r,R)\) with
\[
  \sqrt{q}/\alpha \ <\ r \ <\ R \ <\ \alpha\sqrt{q},
\]
chooses random phases, inverse-embeds to the coefficient domain, and rounds to obtain \((f,g)\in\R^2\). By selecting a
``middle'' annulus window (see \cite{EPRINT:ENSTW23}) one ensures that the rounded trapdoor satisfies the desired
\(\alpha\)-window with high probability and with modest repetition.

\subsection{Hybrid two-plane sampler (details)}
\label{subsec:hybrid-sampler}
We sketch the two-plane hybrid sampler in the notation of \cite{EPRINT:ENSTW23}. Let \(\mathsf{td}_A\) encode an
NTRU trapdoor for \(A\) and let \(t\in\Rq^n\) be the target. Write \(\langle\cdot\rangle_q\) for signed coefficient lift.


\begin{algorithm}[H]
\caption{\(\SampPre(\mathsf{td}_A,t)\): two-plane hybrid sampler (sketch)}
\label{alg:samppre}
\begin{algorithmic}[1]
\State Lift \(t\) to signed coefficients and set \(c \gets \langle t\rangle_q\in(-\frac{q}{2},\frac{q}{2}]^n\).
\State Using \(\mathsf{td}_A\), compute per-slot widths \(\sigma_k[i]\) (two planes) calibrated to trapdoor quality.
\Repeat
  \State Sample slot-wise Gaussian pairs on the two planes, reconstruct a coefficient-domain candidate \(u\).
  \State Accept iff the norm predicate holds for \(u\) (e.g., \(\ell_2\) and/or \(\ell_\infty\) bound).
\Until{accepted}
\State \Return \(u\).
\end{algorithmic}
\end{algorithm}

\paragraph{Public relations.}
Downstream verification and proofs use only the public relation \(A u=t\) and shortness of \(u\) bounded by
\(\BoundSig\).  The value of \(\BoundSig\) must be derived from the sampler's accepted-output tail bound and
converted to the coefficient \(\ell_\infty\)-norm convention used in the ARC relations.
