\section{Extended Parameter Discussion}
\label{app:ext-params}

This appendix records parameter checks for the committed-message issuance relation, the compact MLWE-hiding
commitment, and the SmallWood statement inventory.

\subsection{Admissibility checklist}
A parameter tuple is \emph{admissible} for ARC-SPRUCE if it simultaneously satisfies:
\begin{enumerate}[leftmargin=1.25em]
  \item \textbf{Bound vs. modulus:} \(\BoundMsg \ll q\) so membership checks on
  \([-\BoundMsg,\BoundMsg]\) do not wrap modulo \(q\).
  \item \textbf{Commitment hiding:} the distribution \((A_s,A_s s+e)\) satisfies the Module-LWE hiding
  assumption for the selected \((R,q,n_c,k_s,\chi_s,\chi_e)\).
  \item \textbf{Commitment binding:} double openings are covered by the Module-SIS binding assumption for
  \([C_M\mid A_s\mid I_{n_c}]\), input length \(L_{\mathsf{bind}}=\ell_M+k_s+n_c\), and bound
  \(\beta_{\mathsf{bind}}\).
  \item \textbf{Sampler interface:} the trapdoor/preimage layer satisfies Definition~\ref{def:trapdoor-suite},
  including the public \(\ell_\infty\) shortness bound \(\BoundSig\).
  \item \textbf{Rational-hash guard:} denominator invertibility failure for \(B_3-\mathbf 1_nx_1\) is negligible or
  explicitly carried as the rational-hash admissibility error \(\delta\).
  \item \textbf{SmallWood degree/soundness:} the DECS/LVCS/PCS/PIOP degree bounds and soundness parameters are
  computed for the actual issuance and showing relations.
  \item \textbf{PRF key space and tag length:} the relation enforces \(\veck\in\mathcal K_{\mathsf{key}}\), the PRF
  assumption is made for this same key space, and \(\ell_{\mathsf{tag}}\) is large enough for the intended tag length.
\end{enumerate}

\subsection{Sampler budgets}
Let \(\eta_\varepsilon(\Lambda)\) denote the smoothing parameter of a lattice \(\Lambda\). A sufficient condition for
the preimage distribution used by the signature import is to choose Gaussian widths above the relevant smoothing
floor, with slack.  For the ambient lattice \(\Z^{2N}\) one may use the classical bound
\[
  \eta_\varepsilon(\Z^{2N})
  =
  \sqrt{\ln\!\bigl(4N(1+2^\lambda)\bigr)/\pi}.
\]
In the sampler tuning, trapdoor quality \(\alpha\) and acceptance parameters are chosen so that the output shortness
bound \(\BoundSig\) holds with overwhelming probability.

\subsection{Primary lattice and commitment profile}
Table~\ref{tab:lattice-params} records the primary profile used for the row-inventory discussion.

\begin{table}[H]
\centering
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Knob / Result} & \textbf{Symbol} & \textbf{Value} \\
\midrule
Ring degree & \(N\) & \(512\) \\
Modulus & \(q\) & \(1017857\) \\
Semantic message length & \(\ell_M\) & \(1\) \\
Commitment secret length & \(k_s\) & \(2\) \\
Commitment target length & \(n_c\) & \(1\) \\
Message/randomness bound & \(\BoundMsg\) & \(8\) \\
MLWE sample dimension & \(m_{\mathsf{LWE}}\) & \(Nn_c=512\) \\
MSIS input dimension & \(m_{\mathsf{SIS}}\) & \(N(\ell_M+k_s+n_c)=2048\) \\
MLWE hiding estimate & -- & \(194.408\) bits \\
MSIS binding estimate & -- & \(427.780\) bits \\
\midrule
Trapdoor quality & \(\alpha\) & to be tuned for the sampler \\
Signature bound & \(\BoundSig\) & derived from sampler tail bound \\
\bottomrule
\end{tabular}
\caption{Primary lattice and commitment parameters.}
\label{tab:lattice-params}
\end{table}

For this profile,
\[
  C_M\in\Rq,
  \qquad
  A_s\in\Rq^{1\times2},
  \qquad
  c=C_MM+A_{s,1}s_1+A_{s,2}s_2+e.
\]
The binding length is
\[
  L_{\mathsf{bind}}=4,
\]
and if \(\beta_{\mathsf{msg}}=8\) for all opened small coordinates, the double-opening bound is
\[
  \beta_{\mathsf{bind}}=16.
\]

\subsection{Compact candidate profile}
A smaller-ring candidate is shown in Table~\ref{tab:compact-profile}.  It keeps the same modulus and coefficient
bound, increases \(k_s\), and reduces \(N\).

\begin{table}[H]
\centering
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Knob / Result} & \textbf{Symbol} & \textbf{Value} \\
\midrule
Ring degree & \(N\) & \(256\) \\
Modulus & \(q\) & \(1017857\) \\
Semantic message length & \(\ell_M\) & \(1\) \\
Commitment secret length & \(k_s\) & \(4\) \\
Commitment target length & \(n_c\) & \(1\) \\
Message/randomness bound & \(B\) & \(8\) \\
MLWE sample dimension & \(m_{\mathsf{LWE}}\) & \(Nn_c=256\) \\
MSIS input dimension & \(m_{\mathsf{SIS}}\) & \(N(\ell_M+k_s+n_c)=1536\) \\
MLWE hiding estimate & -- & \(\approx 194.4\) bits \\
\bottomrule
\end{tabular}
\caption{Compact candidate profile.  A binding estimate must be inserted before using this profile as a full concrete
commitment-security profile.}
\label{tab:compact-profile}
\end{table}

\subsection{SmallWood soundness terms}
SmallWood's soundness is a combination of DECS polynomial binding, LVCS/PCS binding, PIOP sampling errors, and
Fiat--Shamir/grinding terms~\cite{EPRINT:FenRiv25b}.  For parameters
\((N_{\mathrm{tree}},s,\ell,\ell',\rho,\eta)\), field \(\F\), and degree bounds
\(d_{\mathrm{decs}}=s+\ell-1\) and \(d_Q\), schematic source-compatible terms include
\[
\varepsilon_{\mathrm{decs}}
=
\binom{N_{\mathrm{tree}}}{d_{\mathrm{decs}}+2}|\F|^{-\eta}
+
\frac{Q_{\RO}^2}{2^{2\lambda}},
\qquad
\varepsilon_{\mathrm{sum}} = |\F|^{-\rho},
\qquad
\varepsilon_{\mathrm{tail}} =
\frac{\binom{d_Q}{\ell'}}{\binom{|S|}{\ell'}}.
\]
The final knowledge-soundness bound for ARC-SPRUCE must instantiate the exact SmallWood-ARK theorem with the
actual row inventory, the actual \(d_Q\), the Fiat--Shamir query bounds, and the grinding parameters.  The showing
statement includes the bilinear inverse check together with a linear signature equation and the PRF effective degree
(Appendix~\ref{app:prf}).

\subsection{SmallWood knobs}
For the issuance and showing proofs discussed in Section~\ref{sec:parameters}, one example parameter tuple is:
\[
  (s,\ell,\ell',\rho,\theta,\eta)=(16,25,2,2,4,19),
\]
with masking degree \(d_Q\) derived from the instantiated constraint degrees.  This tuple is not a final proof-size
claim for the ARC-SPRUCE relation.

\subsection{Extended benchmark grid}
For additional context on how SmallWood knobs affect proof size and proving time, Table~\ref{tab:results-grid}
reports an example sweep over packing and soundness parameters for standalone SmallWood-style statements.  These
figures are not a final ARC-SPRUCE proof-size claim unless the row inventory, constraint degrees, PRF checkpoint
schedule, and Fiat--Shamir soundness terms are instantiated for the exact ARC relations.

\begin{table}[H]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{r r r r r r r r r}
\toprule
\textbf{ProofKB} & \textbf{Time (s)} & \textbf{Bits} & \textbf{NCols} & \(\ell\) & \(\ell'\) & \(\rho\) & \(\theta\) & \(\eta\)\\
\midrule
\ \ 9.32 & 0.266 & 133.44 & 6 & 22 & 2 & 2 & 4 & 17 \\
10.07 & 0.228 & 146.93 & 4 & 24 & 2 & 2 & 4 & 17 \\
11.52 & 0.250 & 133.22 & 4 & 28 & 2 & 2 & 4 & 17 \\
\midrule[1.2pt]
14.06 & 0.630 & 198.01 & 4 & 34 & 8 & 5 & 2 & 26 \\
14.17 & 0.654 & 192.26 & 6 & 34 & 8 & 5 & 2 & 26 \\
14.24 & 0.670 & 198.48 & 4 & 34 & 8 & 6 & 2 & 26 \\
\bottomrule
\end{tabular}
\caption{Example sweep over SmallWood knobs for standalone parameter exploration.  Sizes exclude public parameters and
are not a final ARC-SPRUCE proof-size claim.}
\label{tab:results-grid}
\end{table}
